---
title: "Simulation Study-2"
author: "Anonymous"
date: "`r Sys.Date()`"
output: 
  html_document:
     toc: true
     toc_depth: 2
     toc_float: true
     code-link: true
     code-tools: true
     code_folding: show
     code_download: true
     code-overflow: "scroll"
     self-contained: true
     number_sections: false
     df_print: paged
bibliography: "CPT_LA_new.bib"  
csl: "apa.csl"
---

```{r setup, include=FALSE}
# plot parameters
BIAS_BOUND <- c(-1500L, 1500L)
RMSE_BOUND <- c(NA, 3000L)
PIC_HEIGHT <- 7
PIC_WIDTH <- 13

knitr::opts_chunk$set(
	echo = TRUE,
	fig.align = "center",
	fig.height = PIC_HEIGHT,
	fig.width = PIC_WIDTH,
	warning = FALSE,
	rows.print=11,
	paged.print=TRUE
)
```

```{r lib, message=FALSE, include=FALSE}
library(tidyverse)
library(DT)
library(glue)
library(magrittr)
library(patchwork)
library(kableExtra)
# import functions
source(here::here("functions", "player_and_lotteries.R"))
source(here::here("functions", "new_game.R"))
source(here::here("functions", "analysis_functions.R"))
# ggplot settings
theme_set({
  theme_bw()+    
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 17),
    legend.text = element_text(size = 17),
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text = element_text(size = 14),
    title = element_text(size = 18))
})
```

# Simulation Setting(Code Part)

```{r params}
# Simulation Parameters
Nsim <-  1000L
.phi <-  0.0367 # err = 1e-8, 0.027513126 is err = 1e-6
param <-  list("alpha"=.88, "beta"=.88, "lambda"=2.25, "wp"=.5, "wn"=.5)
exp_param <- list(
  init_values =
    list("G"= 2000L,
         "g"=300L, "l"=-300L),
  random_init = FALSE,
  fix_bnd_width = FALSE,
  n_est = 3L + (6*2L),
  min_step = 0L,
  step_size = 320L
)
mix_param <- list(
  est_method = "ASA", # changed method type: ASA, UD
  start_crit = 500L, # Bisection 3 Times
  start_step = 100L, # ASA_c = 2*100
  stop_rev_times = 3L,
  UseMidrunEst = TRUE 
) 
phi_vec <-  c(.phi*10, .phi, .phi*0.1)
phi_names <- c("large", "medium","small")

# methods
method_levels <- c(
  as.vector(
    outer(c("Bisection", "Bisection-Slider", "MOBS"),
          c("", "_adaptiveBnd"),
          paste0
         )
    ),
  as.vector(
    outer(c("ASA", "PEST", "SimpBisection"),
          c("", "_randInit"),
          paste0
          )
    ),
  "Bisection-ASA", "Bisection-ASA_adaptiveBnd"
  )

method_labels <- (function(x) {
  # Apply regex-based substitutions for base method names
  x <- gsub("^Bisection-Slider", "BiM-S", x)
  # Then replace Bisection (not followed by -Slider)
  x <- gsub("^Bisection", "BiM", x)
  x <- gsub("^BiM-ASA$", "BiM-ASA_fixbnd", x)
  x <- gsub("^SimpBisection", "HaB", x)
  #
  x <- ifelse(grepl("^(BiM|BiM-S|MOBS)$", x), paste0(x, "_fixbnd"), x)
})(method_levels)

# Exclude AdaptiveBound, randInit, and Bisection-ASA
method_levels.woAdapt <- method_levels[!grepl("adaptive|-ASA|ASA$|PEST$|HaB$", method_levels)]
method_labels.woAdapt <- method_labels[!grepl("adaptive|-ASA|ASA$|PEST$|HaB$", method_labels)]
```

## Directories

```{r dir_params}
dir_name <- here::here("simulated_data")
pic_path <- here::here("Results_figs")
if (!dir.exists(pic_path)) {
  dir.create(pic_path, recursive = TRUE)
}
```

# Simulation 2 (new)

The simulation data is stored as a `data.frame`, making it easier to process.

-   `Bisecition-ASA` is newly added.

## Read file and Preprocess

```{r read_early_stop}
# Find the most recent simulation file matching the pattern
file_name <- 
  list.files(dir_name, pattern = "Study2_simulation.*\\.rds", full.names = FALSE) %>%
  sort() %>%
  tail(1)  # Get the most recent file (assuming filenames sort chronologically)

# Print the file found for verification
cat("Using simulation file:", file_name, "\n")

fname <- file.path(dir_name, file_name)

early_df <-
  readRDS(fname) %>% 
  separate_wider_delim(
    method_type,
    delim = "_early",
    names = c("method", "early_stop")
    ) %>% 
  select(phi, method, alpha:lambda, Nsim, any_of("early_stop"),
         matches("^x[1-9](pos|neg)_est")) %>% 
  rename_with(\(x) str_remove(x, "_est")) %>% 
  add_column(x0 = 0L, .before = "x1pos")

# Count the invalid points
cat("Invalid data information")
early_df %>%
  group_by(method, lambda, phi, early_stop) %>%
  summarise(
    num_Inf = sum(rowSums(across(x1pos:x6neg, is.infinite)) > 0),
    num_na = sum(rowSums(across(x1pos:x6neg, is.na)) > 0),
            .groups = 'drop'
    ) %>% 
  filter(num_na!=0) %>%
  print()

# Add true value
early_df <- early_df %>%
  # Filter invalid data points
  filter(!rowSums(across(x1pos:x6neg, is.na)) > 0) %>%
  nest(data = !c(alpha:lambda)) %>%
  rowwise() %>%
  mutate(
    truev = list(
      find_optimal_params(
        params = list(
          "alpha" = alpha, "beta" = beta, "lambda" = lambda, "wp" = 0.5, "wn" = 0.5
          ),
        exp_params_init = exp_param$init_values,
        x_num = exp_param$n_est)
      )
    ) %>%
  ungroup() %>%
  unnest_wider(truev, names_sep = "_") %>%
  select(!matches("truev_(L(_2)?|G_2|lambda_KW)$")) # L, L2 G2 orlambdaKW

# unnest and pivot_longer
true_df <- early_df %>%
  add_column(truev_x0 = 0) %>% 
  pivot_longer(
    cols = starts_with("truev"), 
    names_to = "utility",
    values_to = "true_value") %>% 
  mutate(utility = utility |>
           str_remove("^truev_")|>
           factor(labels = -6:6, levels = gen_util_levels())
         ) %>% 
  select(!data)

cleaned_df <- early_df %>%
  select(alpha: data) %>% 
  unnest(data) %>%
  utility_longer() %>% 
  left_join(true_df, by = join_by(alpha, beta, lambda, utility)) %>%
  mutate(method = gsub("_mix", "-", method),
         early_stop = as.numeric(early_stop)
         )
```

## Bias and RMSE

Compute Bias and RMSE

```{r}
early.bias_RMSE <- cleaned_df %>% 
  filter(utility != 0) %>% 
  group_by(phi, method, utility, early_stop, lambda) %>% 
  summarise(
   bias = mean(x_value - true_value)|> round(),
   RMSE = 
     (x_value - true_value)^2 |> 
     mean() |>
     sqrt() |>
     round(),
   .groups = "drop"
   ) %>% 
  mutate(
    method =
      factor(method,
             levels = method_levels,
             labels = method_labels
             ),
    early_stop = as.factor(early_stop)
  )
```

The results show that simplified Bisection (`SimpBisection`) performs similarly to Bisection, in terms of RMSE.

### Plot Function

```{r}
# Define a wrapper function for plotting
plot_early_bias_RMSE <- function(data, y_var, title, hline_value, 
                                 combine_first_two_rows = TRUE, 
                                 global_var_name = NULL) {
  
  # Set default global variable name based on y_var if not provided
  if (is.null(global_var_name)) {
    global_var_name <- paste0("global_y_ranges_", y_var)
  }
  
  # Calculate y-range for phi levels
  y_ranges <- data %>%
    group_by(phi) %>%
    summarise(
      y_min = min(!!sym(y_var), na.rm = TRUE),
      y_max = max(!!sym(y_var), na.rm = TRUE),
      .groups = 'drop'
    )
  
  # Make first two phi levels have the same range (optional)
  if (combine_first_two_rows && nrow(y_ranges) >= 2) {
    combined_min <- min(y_ranges$y_min[1:2])
    combined_max <- max(y_ranges$y_max[1:2])
    y_ranges$y_min[1:2] <- combined_min
    y_ranges$y_max[1:2] <- combined_max
  }
  
  # For separate plots (when data is filtered), use global ranges from the original full dataset
  # This ensures consistent scaling across separate plots
  if (!exists(global_var_name, envir = .GlobalEnv)) {
    # Store global ranges in the global environment for separate plots to use
    assign(global_var_name, y_ranges, envir = .GlobalEnv)
  }
  
  # Use global ranges if they exist (for separate plots)
  if (exists(global_var_name, envir = .GlobalEnv)) {
    y_ranges_to_use <- get(global_var_name, envir = .GlobalEnv)
    # Match the phi levels present in current data with global ranges
    y_ranges <- y_ranges %>%
      select(phi) %>%
      left_join(y_ranges_to_use %>% select(phi, y_min, y_max), by = "phi")
  }
  
  # Add y-range info to data
  data_with_ranges <- data %>%
    left_join(y_ranges, by = "phi")
  
  ggplot(data_with_ranges, aes(x = utility)) +
    geom_line(aes(
      x = utility,
      y = !!sym(y_var),
      color = early_stop,
      group = early_stop),
      linewidth = 1.2,
      alpha = 0.8
    ) +
    geom_hline(yintercept = hline_value, color = "grey20", lty=2, alpha=0.8) +
    geom_point(
      aes(
        y = !!sym(y_var),
        color = early_stop,
        shape = early_stop),
      size = 3
    ) +
    # Add invisible points to force consistent y-axis ranges within each row
    geom_point(aes(y = y_min), alpha = 0, size = 0) +
    geom_point(aes(y = y_max), alpha = 0, size = 0) +
    facet_grid(rows = vars(phi),
               cols = vars(method),
               scales = "free_y"
    ) +
    scale_x_discrete(labels = latex_labels) +
    scale_shape_manual(
      values = c("5" = 16, "10" = 17)) +
    labs(
      x = expression(x[i]),
      y = title,
      color = "Iteration Number",
      shape = "Iteration Number",
      # title = paste(title, "(Fixed Iteration)")
    ) +
    theme(
      axis.text.y = element_text(size=14)
    )
}
```

### Bias (Figure 5)

```{r bias_early, fig.height=PIC_HEIGHT, fig.width=PIC_WIDTH}
p.bias <- early.bias_RMSE %>%
  filter(method %in% method_labels.woAdapt & !grepl("^Bisection-ASA", method)) %>%
  plot_early_bias_RMSE("bias", "Bias", 0) +
  coord_cartesian(ylim = BIAS_BOUND)

pname <- "study2_bias.pdf"
save_fig(pname, width = PIC_WIDTH, height = PIC_HEIGHT, p_path = pic_path)
```

### RMSE (Figure 6)

```{r RMSE_early, fig.height=PIC_HEIGHT, fig.width=PIC_WIDTH}
p.RMSE <- early.bias_RMSE %>%
  filter(method %in% method_labels.woAdapt & !grepl("^Bisection-ASA", method)) %>%
  plot_early_bias_RMSE("RMSE", "RMSE", 0, combine_first_two_rows = FALSE) +
  coord_cartesian(ylim = RMSE_BOUND)

pname <- "study2_RMSE.pdf"
save_fig(pname, width = PIC_WIDTH, height = PIC_HEIGHT, p_path = pic_path)

```

### relative RMSE



```{r rRMSE_early, fig.height=6, fig.width=18}
p.rRMSE <- early.bias_RMSE %>% 
  group_by(phi, utility, early_stop) %>%
  mutate(
    relative_RMSE = RMSE / RMSE[method == "BiM_fixbnd"],
    early_stop = as.factor(early_stop)
  ) %>% 
  filter((method %in% method_labels.woAdapt) & method != "BiM_fixbnd")  %>% 
  plot_early_bias_RMSE("relative_RMSE", "Relative RMSE to Biscetion", 1)

pname <- "study2_relativeRMSE.pdf"
save_fig(pname, width = 18, height = 6, p_path = pic_path)

```

## Plots with Adaptive Bound

This section provides additional analysis with adaptive bound schemes in bisection-based methods.

*Note:* The plots are not included in the main text.

### Bias

```{r, fig.height=13, fig.width=14}
# First, ensure global ranges are calculated from the full dataset for bias
# This creates the global_y_ranges_bias that both plots will use
# combine_first_two_rows = TRUE means first two rows will have the same range
invisible(early.bias_RMSE %>% 
  plot_early_bias_RMSE("bias", "Bias", 0, 
                       combine_first_two_rows = TRUE, 
                       global_var_name = "global_y_ranges_bias"))

p.bias1 <- early.bias_RMSE %>% 
  filter(grepl("^(BiM)|(MOBS)", method)) %>%
  plot_early_bias_RMSE("bias", "Bias", 0, 
                       combine_first_two_rows = TRUE, 
                       global_var_name = "global_y_ranges_bias") +
  ggtitle("Bisection-based Methods") +
  theme(title = element_text(size = 16))

p.bias2 <- early.bias_RMSE %>% 
  filter(!grepl("^(BiM)|(MOBS)", method)) %>%
  plot_early_bias_RMSE("bias", "Bias", 0, 
                       combine_first_two_rows = TRUE, 
                       global_var_name = "global_y_ranges_bias") +
  ggtitle("Non-bisection Methods and SimpBisection") +
  theme(title = element_text(size = 16))

p.bias1 / p.bias2  +
  plot_annotation(
    title = 'Bias in Study 2: Fixed Number of Iterations',
    theme = theme(plot.title = element_text(size = 28, hjust = .5))) +
  plot_layout(guides = 'collect',
              axes = 'collect'  # This collects both x and y axes
              )
```

```{r, fig.height=13, fig.width=14}
# First, ensure global ranges are calculated from the full dataset for RMSE
# This creates separate global ranges for RMSE (different from bias)
# combine_first_two_rows = FALSE means each row will have its own optimal range
invisible(early.bias_RMSE %>% 
  plot_early_bias_RMSE("RMSE", "RMSE", 0, 
                       combine_first_two_rows = FALSE, 
                       global_var_name = "global_y_ranges_RMSE"))

p.RMSE1 <- early.bias_RMSE %>% 
  filter(grepl("^(BiM)|(MOBS)", method)) %>%
  plot_early_bias_RMSE("RMSE", "RMSE", 0, 
                       combine_first_two_rows = FALSE, 
                       global_var_name = "global_y_ranges_RMSE") +
  ggtitle("Bisection-based Methods") +
  theme(title = element_text(size = 16))

p.RMSE2 <- early.bias_RMSE %>% 
  filter(!grepl("^(BiM)|(MOBS)", method)) %>%
  plot_early_bias_RMSE("RMSE", "RMSE", 0, 
                       combine_first_two_rows = FALSE, 
                       global_var_name = "global_y_ranges_RMSE") +
  ggtitle("Non-bisection Methods and SimpBisection") +
  theme(title = element_text(size = 16))

p.RMSE1 / p.RMSE2  +
  plot_annotation(
    title = 'RMSE in Study 2: Fixed Number of Iterations',
    theme = theme(plot.title = element_text(size = 28, hjust = .5))) +
  plot_layout(guides = 'collect',
              axes = 'collect'  # This collects both x and y axes
              )
```

## Loss Aversion

### Preprocess

```{r early_LA}
# compute True LA coef. values
trueLA_df <- early_df %>% 
  select(!data) %>% 
  mutate(KW = - truev_x1pos / truev_x1neg) %>%
  pivot_longer(cols = matches(".*[1-9][pos|neg]"),
                 names_to = c("trial", "type"),
                 names_pattern = "x(\\d)(.*)",
                 values_to = "value") %>%
  mutate(
    trial = as.integer(trial),
    type = ifelse(type == "pos", "gain", "loss")  # Assign gain/loss
  ) %>% 
  pivot_wider(names_from = type, values_from = value) %>%
  nest(data = c(trial, gain, loss))

trueLA_df <- trueLA_df %>% 
  mutate(
    KT = map(data, ~ KT2(.x)),
    .keep = "unused"
    ) %>%
  unnest_wider(KT, names_sep = "_") %>% 
  pivot_longer(cols = KW:KT_median,
               names_to = "LA_type",
               values_to = "true_LA_est") %>%
  rename(true_KT_classification = "KT_classification")
```

### Compute LA coef from simulation data

```{r LA2}
loss_aver_file_name <- "Study2_LA_df.rds"
file_path <- file.path(dir_name, loss_aver_file_name)

if (file.exists(file_path)) {
  LA_result <- read_rds(file_path)
  print(paste("File read from:", file_path))
} else {
  library(furrr)
  LA_result <- early_df %>% 
    select(!starts_with("true")) %>% 
    unnest(cols = c(data)) %>% 
    mutate(KW = -x1pos/x1neg)
  
  LA_result <- LA_result %>% 
    pivot_longer(cols = matches(".*[1-9][pos|neg]"),
                   names_to = c("trial", "type"),
                   names_pattern = "x(\\d)(.*)",
                   values_to = "value") %>%
    mutate(
      trial = as.integer(trial),
      type = ifelse(type == "pos", "gain", "loss")  # Assign gain/loss
    ) %>% 
    pivot_wider(names_from = type, values_from = value) %>%
    nest(data = c(trial, gain, loss))
  plan(multisession)
  # Measure system time for paralleled processing
  print(Sys.time())
  tm <- system.time({
    LA_result <- LA_result %>%
      # debug for small data
      # slice_sample(n = 500) %>% 
      mutate(
        # stores median, mean and classification of KT
        # this may cause duplication in interpolation `approx` function
        KT = future_map(data, ~ KT2(.x)),
        .keep = "unused"
      ) %>%
      unnest_wider(KT, names_sep = "_") %>% 
      pivot_longer(cols = KW:KT_median,
                   names_to = "LA_type",
                   values_to = "LA_est")
  })
  print(tm)
  # Save LA_result as an RDS file
  saveRDS(LA_result, file = file_path)
  print(paste("File saved at:", file_path))
}

```

```{r}
LA_result <- LA_result %>%
  select(!x0) %>% 
  left_join(trueLA_df, by = join_by(alpha, beta, lambda, LA_type)) %>% 
  mutate(
    early_stop = as.numeric(early_stop),
    method = gsub("_mix", "-", method),
    method =
      factor(method,
             levels = method_levels,
             labels = method_labels
             )
    )
```

### Compute 95% CI

```{r include=FALSE}
custom_shapes <- c(rep(21, 6), 24, 24, 25, 24, 24, 25, 21, 21)
names(custom_shapes) <- method_labels
custom_shapes.woAdapt <- custom_shapes[!grepl("adaptive", method_levels)]
custom_shapes.woAdapt <- custom_shapes[!grepl("adaptive|-ASA|ASA$|PEST$|HaB$", method_labels)]

```

- Rank the CI width b/t 3 different loss aversion indices: `KT_mean`, `KT_median`, `KW`

- `KW` generally has the smallest CI width, especially when $\phi$ is large and medium.

```{r}
LA_result %>%
  filter(method %in% method_labels.woAdapt,
         is.finite(LA_est),
         early_stop == 10,
         LA_type != "KT_reg") %>%
  group_by(phi, method, LA_type) %>%
  summarise(
    CI_lower = quantile(LA_est, 0.025, na.rm = TRUE),
    CI_upper = quantile(LA_est, 0.975, na.rm = TRUE),
    CI_width = CI_upper - CI_lower,
    .groups = "drop"
  ) %>%
  select(phi, method, LA_type, CI_width) %>%
  pivot_wider(
    names_from = LA_type,
    names_glue = "{LA_type}_CIwidth",
    values_from = CI_width
  ) %>%
  rowwise() %>%
  mutate(
    # Create row-wise ranking of CI widths
    CI_width_ranks = list(rank(c_across(ends_with("CIwidth")))),
    # Extract individual ranks for each type
    KT_mean_rank = CI_width_ranks[1],
    KT_median_rank = CI_width_ranks[2],
    KW_rank = CI_width_ranks[3],
  ) %>%
  ungroup() %>%
  # relocate(ends_with('rank'), .after = method) %>% 
  arrange(phi, method)
```

### 95% CI (Figure 7)

```{r fig.height=9, fig.width=10}
LA_result %>% 
  filter(method %in% method_labels.woAdapt,
             is.finite(LA_est),
             early_stop == 10,
             LA_type != "KT_reg") %>%
    mutate(
      early_stop = factor(as.numeric(early_stop)),
      # Reverse the factor levels of method according to reversed method_labels.woAdapt
      method = factor(method, levels = rev(method_labels.woAdapt))
      ) %>%
    group_by(phi, method, LA_type, early_stop) %>%
    ggplot() +
    geom_vline(
      aes(xintercept = true_LA_est),
      lty = 2, color = "grey30", linewidth = 1.05
    ) +
    stat_summary(
      aes(x = LA_est, y = method, color = method),
      geom = "errorbar",
      position = position_dodge(0.6),
      fun.min = \(x) quantile(x, 0.025, na.rm = TRUE),
      fun.max = \(x) quantile(x, 0.975, na.rm = TRUE),
      linewidth = 1.2, width = 0.5
    ) +
    stat_summary(
      aes(x = LA_est, y = method, fill = method, shape = method, color = method),
      position = position_dodge(0.6),
      fun = \(x) mean(x, na.rm = TRUE),
      geom = "point",
      size = 3.0
    ) +
    facet_grid(phi ~ LA_type, 
               # scales = "free"
               ) +
    scale_x_continuous(
      transform = scales::pseudo_log_trans(base = 10),
      breaks = c(-20, -10, -5, 0, 1, 5, 10, 20, 40)
    ) +
    scale_shape_manual(values = custom_shapes) +   # Custom shape mapping
    labs(
      x = "Loss Aversion Indices",
      y = "Methods",
      # title = "Loss Aversion Coefficients Estimates (Iteration = 10)"
    ) +
    theme(
      panel.spacing.x = grid::unit(1, "lines"),     # Adjusts horizontal spacing
      legend.title = element_blank(),
      legend.text = element_text(size = 14)
    )+
    guides(
      colour = "none",
      shape  = "none",
      fill = "none"
  )

pname <- "study2_LA_Summary_iter10.pdf"
save_fig(pname, width = 11, height = 9, p_path = pic_path)
```

### Bias and RMSE

*Note:* These figures are not included in the main text

```{r}
LA_summ <- LA_result %>% 
  filter(is.finite(LA_est)) %>%  
  # filter(!grepl("randInit$", method)) %>%
  group_by(lambda, phi, method, LA_type, early_stop) %>% 
  summarise(
    bias = mean((LA_est - true_LA_est), na.rm = TRUE),
    RMSE = mean((LA_est - true_LA_est)^2, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  group_by(phi, LA_type, early_stop) %>% 
  mutate(relative_RMSE = RMSE / RMSE[method == "BiM_fixbnd"]) %>% 
  ungroup()
```

```{r plot_LA}
plot_LA <- function(data, var_y, subset_filter) {
  y_label <- rlang::as_label(rlang::enquo(var_y)) %>%   # Convert to string
    stringr::str_to_sentence()
  
  data %>%
    filter({{ subset_filter }},
           is.finite({{ var_y }}),
           early_stop == 10,
           LA_type != "KT_reg") %>%
    mutate(early_stop = as.factor(early_stop)) %>%
    ggplot(aes(x = method)) +
    geom_hline(yintercept = 0, color = "grey30", lty = 2, alpha = 0.8) +
    geom_point(
      aes(y = {{ var_y }}, fill = method, color = method, shape = method),
      position = position_dodge(width = 0.4),
      size = 3.0
    ) +
    facet_grid(
      rows = vars(phi),
      cols = vars(LA_type),
      scales = "free_y"
    ) +
    scale_shape_manual(values = custom_shapes) +
    labs(
      x = "Method",
      y = y_label,
      title = glue("Loss Aversion Coefficients: {y_label} (Iteration = 10)")
    ) +
    theme(
      legend.title = element_blank(),
      legend.text = element_text(size = 14),
      axis.text.x = element_text(size = 11, angle = 90, vjust = 0.55),
      strip.text = element_text(size = 13)
    )
}
```

```{r, fig.height=9, fig.width=9}
LA_summ %>% 
  plot_LA(bias, !grepl("randInit$", method))
pname <- "study2_LA_bias_iter10woRandInit.pdf"
save_fig(pname, width = 9, height = 9, p_path = pic_path)

LA_summ %>% 
  plot_LA(bias)
pname <- "study2_LA_bias_iter10.pdf"
save_fig(pname, width = 10, height = 9, p_path = pic_path)
```

The cell below shows alternative visualization:

```{r eval=FALSE, fig.width=8, include=FALSE}
# Filter and prepare data
filtered_data <- LA_summ %>%
  filter(is.finite(bias) & early_stop == 10 & LA_type != "KT_reg") %>%
  mutate(early_stop = as.factor(early_stop))

# Define unique facets
facets <- unique(filtered_data %>% select(phi, LA_type))

# Create a list to store individual plots
plot_list <- list()

# Loop over each facet combination
for (i in 1:nrow(facets)) {
  facet_data <- filtered_data %>%
    filter(phi == facets$phi[i], LA_type == facets$LA_type[i])
  
  y_limits <- if (i <= 6) c(-0.5, 1) else c(-2, 4)
  
  p <- ggplot(facet_data, aes(x = method)) +
    geom_hline(yintercept = 0, color = "grey30", lty = 2, alpha = 0.8) +
    geom_point(aes(y = bias, fill = method, color = method, shape = method),
               position = position_dodge(width = 0.4),
               size = 3.0) +
    scale_shape_manual(values = custom_shapes) +  # Custom shape mapping
    labs(x = "Method",
         y = "Bias",
         title = glue("Phi:{facets$phi[i]}; {facets$LA_type[i]}")
         ) +
    ylim(y_limits)+
  # ylim(-1, 1)+  # Set your desired y-axis limits here
    theme(
      # legend.position = "bottom",
      legend.title = element_blank(),
      axis.text.x = element_text(size = 11, angle = 90, vjust = .55),
      strip.text= element_text(size = 11),
      title = element_text(size = 10))
  
  plot_list[[i]] <- p
}

# Combine plots using patchwork
combined_plot <- wrap_plots(
  plot_list,
  ncol = length(unique(filtered_data$LA_type))) +
  plot_annotation(title = "Loss Aversion Coefficients: Bias (Iteration = 10)") +
  plot_layout(axes = "collect",guides = 'collect') &
  theme(legend.position='bottom')
combined_plot
```

#### RMSE

```{r, fig.height=9, fig.width=10}
LA_summ %>% 
  plot_LA(RMSE, !grepl("randInit$", method)) +
  labs(
    y = 'RMSE',
    title = "Loss Aversion Coefficients: RMSE (Iteration = 10)"
  )
pname <- "study2_LA_RMSE_iter10woRandInit.pdf"
save_fig(pname, width = 9, height = 9, p_path = pic_path)

LA_summ %>% 
  plot_LA(RMSE) +
  labs(
    y = 'RMSE',
    title = "Loss Aversion Coefficients: RMSE (Iteration = 10)"
  )
pname <- "study2_LA_RMSE_iter10.pdf"
save_fig(pname, width = 10, height = 9, p_path = pic_path)
```

## Violations of Monotonicity

This section tabulates, by method and $\phi$, the proportion of simulated
participants whose elicited utility points fail monotonicity
($x_6^- \dots \leq x_1^- \leq 0 \leq x_1^+ \dots \leq x_6^+$). Reference rates of stochastic
dominance violations from prior empirical work are:

-   Abdellaoui et al. (2016): not provided
-   Bleichrodt and L'Haridon (2023): 10/122 = `r round(10/122, 3)`

```{r paged.print=TRUE, rows.print=9*2}
monotone_df <- cleaned_df %>% 
  select(!true_value) %>% 
  mutate(utility = as.integer(utility) - 7L) %>% 
  pivot_wider(
    names_from = utility,
    values_from = x_value,
    names_glue = "x{abs(utility)}{case_when(utility > 0 ~ 'pos', 
                                       utility < 0 ~ 'neg', 
                                       TRUE ~ '')}"
  ) %>% 
  relocate(gen_util_levels(6L, FALSE), .after = x0) %>% 
  rowwise() %>%
  mutate(
    violation = is.unsorted(c_across(x6neg:x6pos)),
    ) %>%
  ungroup()

monotone_df %>%
  mutate(early_stop = as.numeric(early_stop),
         method = factor(method, levels = method_levels, labels = method_labels)
         ) %>%
  group_by(phi, early_stop, method) %>%
  summarise(
    # n = n(),
    violation_ratio = glue("{round(sum(violation)/n()*100,1)}%"),
    .groups = "drop"
    ) %>%
  pivot_wider(
    names_from = early_stop,
    names_glue = "Iteration = {early_stop}",
    values_from = violation_ratio
  ) %>%
  filter(!(`Iteration = 5` == "0%" & `Iteration = 10` == "0%"),
         !grepl("adaptive", method) # filter out adaptive
         ) %>%
  arrange(phi, method)
 # %>%
 #  xtable::xtable()
```
