---
title: "Simulation Study-1"
author: "Wei-Chen Chang"
date: "`r Sys.Date()`"
output: 
  html_document:
     toc: true
     toc_depth: 2
     toc_float: true
     code-link: true
     code-tools: true
     code_folding: show
     code_download: true
     code-overflow: "scroll"
     self-contained: true
     number_sections: false
     df_print: paged
bibliography: "CPT_LA_new.bib"  
csl: "apa.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.align = "center",
	warning = FALSE,
	rows.print=11,
	paged.print=TRUE
)
```


```{r lib, message=FALSE, include=FALSE}
library(tidyverse)
library(glue)
library(magrittr)
library(patchwork)
library(kableExtra)
# import functions
source(here::here("functions", "player_and_lotteries.R"))
source(here::here("functions", "analysis_functions.R"))
# ggplot settings
theme_set({
  theme_bw()+
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 17),
    legend.text = element_text(size = 17),
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text = element_text(size = 12),
    title = element_text(size = 18))
})
```


# Simulation Setting(Code Part)

```{r params}
# Simulation Parameters
Nsim <-  1000L
.phi <-  0.0367 # err = 1e-8, 0.027513126 is err = 1e-6
param <-  list("alpha"=.88, "beta"=.88, "lambda"=2.25, "wp"=.5, "wn"=.5)
exp_param <- list(
  init_values =
    list("G"= 2000L,
         "g"=300L, "l"=-300L, "x1+"=1000L),
  random_init = FALSE,
  fix_bnd_width = FALSE,
  n_est = 3L + (6*2L),
  min_step = 0L,
  step_size = 320L
)
mix_param <- list(
  est_method = "ASA", # changed method type: ASA, UD
  start_crit = 500L, # Bisection 3 Times
  start_step = 100L, # ASA_c = 2*100
  stop_rev_times = 3L,
  UseMidrunEst = TRUE 
) 
phi_vec <- c(.phi*10, .phi, .phi*0.1)
names(phi_vec) <- c("large", "medium", "small")

# methods

method_levels <- 
  c("Bisection", "Bisection-Slider", "MOBS", "ASA","SimpBisection", "PEST")
utility_method_levels <- 
          c(
            "Bisection","Bisection_fixbnd",
            "Bisection-Slider", "Bisection-Slider_fixbnd",
            "MOBS", "MOBS_fixbnd",
            "ASA", "ASA_randInit",
            "SimpBisection", "SimpBisection_randInit",
            "PEST", "PEST_randInit")

```

## Directories

```{r dir_params}
# pics and data directories
dir_name <- here::here("simulated_data")
pic_path <- here::here("Results_figs")
if (!dir.exists(pic_path)) {
  dir.create(pic_path, recursive = TRUE)
}
```

# Simulation 1

Read files and preprocess data.
```{r bound2}
file_name <- 
  list.files(dir_name, pattern = "Study1_simulation.*\\.rds", full.names = FALSE) %>%
  sort() %>%
  tail(1)  # Get the most recent file (assuming filenames sort chronologically)

# Print the file found for verification
cat("Using simulation file:", file_name, "\n")

fname <- file.path(dir_name, file_name)

bound_df <- read_rds(fname) %>% 
  rename(method = method_type) %>% 
  select(phi, method, alpha:lambda, Nsim, any_of("early_stop"),
         matches("^x[1-9](pos|neg)_est")) %>% 
  rename_with(\(x) str_remove(x, "_est")) %>% 
  mutate(
    method = sub("Bisection_Slider", "Bisection-Slider", method)
  ) %>% 
  add_column(x0 = 0L, .before = "x1pos")

# Count the invalid points
bound_df %>%
  group_by(method, lambda, phi) %>%
  summarise(
    num_Inf = sum(rowSums(across(x1pos:x6neg, is.infinite)) > 0),
            .groups = 'drop') %>% 
  filter(num_Inf!=0) %>%
  print()

# Add true value
bound_df <- bound_df %>%
  # Filter invalid data points
  filter(!rowSums(across(x1pos:x6neg, is.infinite)) > 0) %>%
  nest(data = !c(alpha:lambda)) %>%
  rowwise() %>%
  mutate(
    truev = list(
      find_optimal_params(
        params = list(
          "alpha" = alpha, "beta" = beta, "lambda" = lambda, "wp" = 0.5, "wn" = 0.5
          ),
        exp_params_init = exp_param$init_values,
        x_num = exp_param$n_est)
      )
    ) %>%
  ungroup() %>%
  unnest_wider(truev, names_sep = "_") %>%
  select(!matches("truev_(L(_2)?|G_2|lambda_KW)$")) # L, L2 G2 orlambdaKW

# unnest and pivot_longer
true_df <- bound_df %>%
  add_column(truev_x0 = 0) %>% 
  pivot_longer(
    cols = starts_with("truev"), 
    names_to = "utility",
    values_to = "true_value") %>% 
  mutate(utility = utility |>
           str_remove("^truev_")|>
           factor(labels = -6:6,
                  levels = gen_util_levels())
         ) %>% 
  select(!data)

cleaned_df <- bound_df %>%
  select(alpha:data) %>% 
  unnest() %>%
  utility_longer() %>% 
  left_join(true_df, by = join_by(alpha, beta, lambda, utility))

```


## Utility Curve Plots

The colored line segments represent the 95% CI of the observations. The black dashed line (and the hollow dots) shows the true values.


```{r, fig.height=7, fig.width=14}
cleaned_df %>% 
  filter(lambda == 2.25 & phi != "small" ) %>%
  mutate(
    method =
      factor(method, levels = utility_method_levels)
  ) %>%
  group_by(phi) %>% 
  ggplot(aes(y = utility)) +
  geom_hline(
    yintercept = 
      as.numeric(
        factor("x0", levels = gen_util_levels()
               )),
    color = "red2",
    linetype = "dashed", alpha = 0.8) +
  # True utility curve
  geom_line(
    aes(y = utility, x = true_value, group = 1),
    color = "black", linetype = "3331") +
  geom_point(
    aes(y = utility, x = true_value, group = 1),
    color = "black", pch = 1, size =2.5) +
  # 95% range
  stat_summary(
    aes(y = utility, x = x_value, color = phi, shape = phi),
    geom = "pointrange",
    fun = \(x) mean(x, na.rm = TRUE),
    fun.min = \(x) quantile(x, .025, na.rm = TRUE),
    fun.max = \(x) quantile(x, .975, na.rm = TRUE),
    position = position_dodge(width = 0.9),
    linewidth = 1.1, size = 0.6, alpha=.8
  ) +
  labs(x = "Elicited x ",
       y = "V(X)",
       title = "Value Curve",
       color = "phi") +
  facet_wrap(~ method, dir="v", ncol=6, nrow=2) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 0.6, vjust=0.6),
    strip.text= element_text(size = 15),
    )

pname <- "study1_utility_curve.pdf"
save_fig(pname, width = 14, height = 7, p_path = pic_path)
```

## Bias and RMSE

This sections summarizes the bias and RMSE of the elicited values compared to the true values.

```{r summ_biasRMSE}
df.bias_RMSE <- cleaned_df %>%
  filter(utility != 0) %>% 
  mutate(
    boundary_type = case_when(
      grepl(".*_fixbnd$", method) ~ "fix_bnd",
      grepl(".*_randInit$", method) ~ "rand_init",
      TRUE ~ "equal_exp"
    ),
    method = 
      str_replace(method, "_(randInit|fixbnd)$", "") |>
      factor(
        levels = method_levels
      )
  ) %>% 
  group_by(phi, method, boundary_type, utility, lambda) %>% 
  summarise(
   bias = mean(x_value - true_value)|> round(),
   RMSE = 
     (x_value - true_value)^2 |> 
     mean() |>
     sqrt() |>
     round(),
   .groups = "drop"
   )
```

### Bias

```{r bias_bnd, fig.height=7, fig.width=13}
p.bias <- df.bias_RMSE %>% 
  filter(lambda == 2.25) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = bias,
    color = boundary_type,
    group = boundary_type),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = 0, color = "grey30", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = bias,
      color = boundary_type,
      shape = boundary_type),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             # scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_color_discrete(
    # values = c("fix_bnd" = "cyan4", "equal_exp" = "orange2"),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variant") +
  scale_shape_manual(
    values = c("fix_bnd" = 16, "equal_exp" = 17, "rand_init" = 15),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variant") +
  labs(x = expression(x["i"]),
       y = "Bias",
       title = "Bias")+
  theme(
    strip.text= element_text(size = 15)
    )

pname <- "study1_bias.pdf"
p.bias
save_fig(pname, width = 13, height = 7, p_path = pic_path)
```


### Bias2

One may suspect that the difference it due to the specification of the value function.
Hence we vary in $\lambda$ in the value function in this section.

-   Theree levels of $\lambda$ are specified: 0.5, 1, 2.25.

```{r bias_vary_lambda, fig.height=14, fig.width=14}
df.tmp <- cleaned_df %>%
  filter(utility != 0) %>% 
  mutate(
    method = case_when(
      method == "Bisection_Slider" ~ "Bisection-Slider",
      method == "Bisection_Slider_fixbnd" ~ "Bisection-Slider_fixbnd",
      TRUE ~ method # Keep other values unchanged
    )
    ) %>% 
  group_by(phi, method, utility, lambda) %>% 
  summarise(
   bias = mean(x_value - true_value)|> round(),
   RMSE = (x_value - true_value)^2 |> 
     mean() |>
     sqrt() |>
     round(),
   .groups = "drop"
   )
helper_plot <- function(df) {
  df %>% ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = bias,
    color = lambda,
    group = lambda),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = 0, color = "grey30", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = bias,
      color = lambda,
      shpae = lambda),
    size = 3) +
  scale_color_brewer(palette = "Dark2")+
  facet_grid(rows = vars(phi),
             cols = vars(method),
             # scales = "free_y"
             ) +
  ylim(-6000, 8000)+
  scale_x_discrete(labels = latex_labels) +
  labs(x = expression(x["i"]),
       y = "Bias")+
  theme(
    strip.text= element_text(size = 14)
    )
}

p1 <- df.tmp %>% 
  filter(grepl("(Bisection|MOBS)", method) & !grepl("(Simp)", method)) %>% 
  mutate(lambda = as.factor(lambda),
         method = factor(
           method,
           levels = c("Bisection", "Bisection_fixbnd",
                      "Bisection-Slider", "Bisection-Slider_fixbnd",
                      "MOBS", "MOBS_fixbnd")
           )) %>%
  helper_plot()

p2 <- df.tmp %>% 
  mutate(lambda = as.factor(lambda)) %>%
  filter(!(grepl("(Bisection|MOBS)", method) & !grepl("(Simp)", method))) %>% 
  helper_plot()

p <- p1 / p2 +
  plot_annotation(title = 'Bias (Varies with Lambda)') +
  plot_layout(guides = 'collect') & 
  theme(legend.position='bottom',
        legend.text = element_text(size=15))
p
pname <- "study1_bias_different_Lambda.pdf"

save_fig(pname, width = 14, height = 14, p_path = pic_path)
```


```{r rm, include=FALSE}
rm(df.tmp)
rm(p1)
rm(p2)
```


### RMSE

```{r}
df.bias_RMSE %>% 
  filter(lambda == 2.25, method =="ASA")
```


```{r RMSE_bnd, fig.height=7, fig.width=13}
p.RMSE <- df.bias_RMSE %>% 
  filter(lambda == 2.25) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = RMSE,
    color = boundary_type,
    group = boundary_type),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = c(0), color = "grey30", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = RMSE,
      color = boundary_type,
      shape = boundary_type),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             # scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_color_discrete(
    # values = c("fix_bnd" = "cyan4", "equal_exp" = "orange2"),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variant") +
  scale_shape_manual(
    values = c("fix_bnd" = 16, "equal_exp" = 17, "rand_init" = 15),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variant") +
  labs(x = expression(x["i"]),
       y = "RMSE",
       title = "RMSE")+
  theme(
    strip.text= element_text(size = 15)
    )

pname <- "study1_RMSE.pdf"
save_fig(pname, width = 13, height = 7, p_path = pic_path)
```


## Bias+RMSE Combined

```{r, fig.height=14, fig.width=14}
p <- p.bias / p.RMSE +
  plot_annotation(
    title = 'Study1: Iterates Until Step Size < 5',
    theme = theme(plot.title = element_text(size = 32, hjust = .5))) +
  plot_layout(guides = 'collect') & 
  theme(legend.position='bottom',
        legend.text = element_text(size = 24),
        legend.title = element_text(size = 26),
        strip.text= element_text(size = 20),
        axis.title.x = element_text(size = 20),
        )

pname <- "study1_biasRMSE.pdf"
p
save_fig(pname, width = 16, height = 16, p_path = pic_path)

```


## Iteration Counts

```{r eval=FALSE, include=FALSE}
len_df <- read_rds(fname) %>% 
  select(alpha:Nsim, ends_with("len")) %>%
  mutate(
    # method = str_replace(method_type, "_(randInit|fixbnd)$", ""),
    method = gsub("Bisection_Slider","Bisection-Slider", method_type) |> 
      factor(levels = utility_method_levels),
    scheme = 
      case_when(
        grepl(".*_fixbnd$", method_type) ~ "Fixed Boundary Width",
        grepl(".*_randInit$", method_type) ~ "Random Initial Points",
        .default = "Equal-Expectation"
        ),
    .after = phi,
    .keep = "unused"
  )

len_df %>% 
  # group_by(phi, lambda,  method, scheme) %>% 
  group_by(phi, lambda,  method) %>% 
  filter(lambda ==2.25) %>% 
  mutate(
    mean_each_step = rowMeans(across(ends_with("len"))),
    .keep = "unused"
  ) %>%
  summarise(
    Mean_Iteration_Number = mean(mean_each_step) |> round(),
    .groups = "drop"
  ) %>% 
  select(!lambda) %>%
  group_by(phi) %>%
  # arrange(desc(Mean_Iteration_Number), .by_group = TRUE)
  arrange(method, .by_group = TRUE) %>% 
  write_csv(
    file = file.path(pic_path, "step.csv")
  )

```

# Inspect alternative termination rule for ASA

-  Since step size < 5 may not be appropriate for ASA (at least 64 iterations to terminate).

-  The `m-reversal-out-of-k` rule is applied. We extract cases where 6 reversals happen in last 8 trials as the final estimate, compute the final trial counts and the estimates.   

```{r}
ASA_df <- read_rds(fname) %>% 
  rename(method = method_type) %>% 
  filter(grepl("^ASA.*", method)) %>% 
  select(!c(L, G2, L2, L_est:x6neg_len)) %>%
  pivot_longer(
    cols = matches("x[1-9](pos|neg)"),
    names_to = "utility",
    values_to = "seq",
    ) %>% 
  mutate(
    utility = factor(utility,
                     labels = -6:6,
       levels = gen_util_levels())
  )
```


```{r}
# Function to find a subvector with at least m unique values in k length
# This function helps us to truncate the sequence with the m-reversal-out-of-k rule
find_subvector <- function(vec, m, k, start.from = 1) {
  # find until a subarray with length of k contains more than m reversals
  n <- length(vec)
  
  if (k > (n - start.from + 1)) {
    stop(
      sprintf("Error: window size k (%d) is greater than the length of vec (%d)", k, n))
  } else if (m > k){
    stop(
      sprintf("Error: window size k (%d) is greater than target reversal times m=(%d)", k, m))
    
  }

  for (i in start.from:(n - k + 1)) {
    sub_vec <- vec[i:(i + k - 1)]
    if (length(unique(sub_vec)) >= m) {
      return(list(
        value = sub_vec[k],
        index = i + k - 1
      ))
    } else if (anyNA(sub_vec)){
      # if NA found, return current idx
        return(list(
        value = sub_vec[k-1],
        index = i + k - 2
      ))
    }
  }

  # if no sub-sequence satisfy the condition, return last element
  return(list(
        value = sub_vec[n],
        index = n
      ))  # No match found
}

# Truncated ASA sequences
sliced_ASA <- ASA_df %>%
  filter(lambda == 2.25, grepl("^ASA.*", method)) %>%
  mutate(step = map(seq, diff),
         # m-reversal-out-of-k rule
         early = map(step, \(x) find_subvector(x, 6, 8)),
         .after = Nsim
         ) %>%
  # unnest early into `value`, `index`
  unnest_wider(early) %>% 
  mutate(
    sliced_seq = map2(seq, index,\(x, idx) x[1:idx]),
    sliced_N_iter = map_int(sliced_seq, length),
    final_step_size = abs(value),
    # extract final est
    x_value = map_int(sliced_seq, \(x) x[length(x)]),
    .keep = 'unused'
  ) %>% 
  left_join(true_df, by = join_by(alpha, beta, lambda, utility))
```

```{r}
sliced_ASA %>%
  group_by(phi, method) %>%
  summarise(mean_iteration_number = mean(sliced_N_iter))
```


A visualization of the sliced ASA results, showing the distribution of the iteration counts across different methods and $\phi$ values.
```{r fig.height=6, fig.width=12}
sliced_ASA %>%
  group_by(phi, method, utility) %>% 
  ggplot() + 
  # geom_violin(
  #   aes(x = sliced_N_iter,
  #       y= utility,
  #       fill = method,
  #       ),
  #   draw_quantiles = c(.25, .5, .75)) + 
  geom_boxplot(
    aes(x = sliced_N_iter,
        y= utility,
        fill = method,
        ),
    draw_quantiles = c(.25, .5, .75)) + 
  # geom_histogram(aes(x = sliced_N_iter, fill = method)) +
  facet_grid(
    . ~ phi
  ) +
  scale_x_continuous(
    breaks = seq(0,200, 15)
  )

```

## Bias & RMSE

```{r}
sliced_ASA.biasRMSE <- sliced_ASA %>% 
  group_by(phi, method, utility, lambda) %>% 
  summarise(
   bias = mean(x_value - true_value)|> round(),
   RMSE = 
     (x_value - true_value)^2 |> 
     mean() |>
     sqrt() |>
     round(),
   .groups = "drop"
   ) %>% 
  mutate(
    boundary_type = case_when(
      grepl(".*_fixbnd$", method) ~ "fix_bnd",
      grepl(".*_randInit$", method) ~ "rand_init",
      TRUE ~ "equal_exp"
    ),
    method = "ASA_sliced",
    .after = method
  )
# add original methods
sliced_ASA.biasRMSE <- sliced_ASA.biasRMSE %>% 
  add_row(
    df.bias_RMSE %>%
      mutate(
        method = as.character(method)
      ) %>% 
      select(any_of(names(sliced_ASA.biasRMSE))) %>% 
      filter(lambda==2.25)
  )
```

```{r}
sliced_ASA.biasRMSE %>% 
  filter(!grepl("^(Bisection|MOBS)", method)) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = bias,
    color = boundary_type,
    group = boundary_type),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = 0, color = "grey30", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = bias,
      color = boundary_type,
      shape = boundary_type),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             # scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_color_discrete(
    # values = c("fix_bnd" = "cyan4", "equal_exp" = "orange2"),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variant") +
  scale_shape_manual(
    values = c("fix_bnd" = 16, "equal_exp" = 17, "rand_init" = 15),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variant") +
  labs(x = expression(x["i"]),
       y = "Bias",
       title = "Bias")+
  theme(
    strip.text= element_text(size = 15)
    )
```
```{r}
sliced_ASA.biasRMSE %>% 
  filter(!grepl("^(Bisection|MOBS)", method)) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = RMSE,
    color = boundary_type,
    group = boundary_type),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = 0, color = "grey30", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = RMSE,
      color = boundary_type,
      shape = boundary_type),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_color_discrete(
    # values = c("fix_bnd" = "cyan4", "equal_exp" = "orange2"),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variant") +
  scale_shape_manual(
    values = c("fix_bnd" = 16, "equal_exp" = 17, "rand_init" = 15),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variant") +
  labs(x = expression(x["i"]),
       y = "RMSE",
       title = "RMSE")+
  theme(
    strip.text= element_text(size = 15)
    )
```


# Additional Analysis: Loss aversion

Although it is possible to estimate the loss aversion coefficient from the elicited values, we did not procced it.

## Preprocess

```{r true_LA, eval=FALSE, include=FALSE}
# compute True LA coef. values
trueLA_df <- bound_df %>% 
  select(!data) %>% 
  mutate(KW = - truev_x1pos / truev_x1neg) %>% 
  pivot_longer(cols = matches(".*[1-9][pos|neg]"),
                 names_to = c("trial", "type"),
                 names_pattern = "x(\\d)(.*)",
                 values_to = "value") %>%
  mutate(
    trial = as.integer(trial),
    type = ifelse(type == "pos", "gain", "loss")  # Assign gain/loss
  ) %>% 
  pivot_wider(names_from = type, values_from = value) %>%
  nest(data = c(trial, gain, loss))

trueLA_df <- trueLA_df %>% 
  mutate(
    KT = map(data, ~KT2(.x)),
    .keep = "unused"
    ) %>% 
  unnest_wider(KT, names_sep = "_") %>% 
  pivot_longer(cols = KW:KT_median,
               names_to = "LA_type",
               values_to = "true_LA_est") %>% 
  rename(true_KT_classification = "KT_classification")
```