---
title: "Bisection Simulation: Whole utility Curve"
author: "Wei-Chen Chang"
date: "`r Sys.Date()`"
output: 
  html_document:
     toc: true
     toc_depth: 2
     toc_float: true
     code-link: true
     code-tools: true
     code_folding: show
     code_download: true
     code-overflow: "scroll"
     self-contained: true
     number_sections: false
     df_print: paged
bibliography: "CPT_LA_new.bib"  
csl: "apa.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.align = "center",
	warning = FALSE,
	rows.print=11,
	paged.print=TRUE
)
```


```{r lib, message=FALSE, include=FALSE}
library(tidyverse)
library(DT)
library(glue)
library(magrittr)
library(patchwork)
library(kableExtra)
# import functions
source("../functions/player_and_lotteries.R")
# source("../functions/TO_exp.R")
theme_set({
  theme_bw()+    
  theme(axis.title = element_text(size = 16),
        # axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text = element_text(size = 13),
        strip.text= element_text(size = 12),
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        title = element_text(size = 18))
})

```


# Simulation Setting(Code Part)

```{r params}
# Simulation Parameters
Nsim <-  1000L
.phi <-  0.0367 # err = 1e-8, 0.027513126 is err = 1e-6
param <-  list("alpha"=.88, "beta"=.88, "lambda"=2.25, "wp"=.5, "wn"=.5)
exp_param <- list(
  init_values =
    list("G"= 2000L,
         "g"=300L, "l"=-300L, "x1+"=1000L),
  random_init = FALSE,
  fix_bnd_width = FALSE,
  n_est = 3L + (6*2L),
  min_step = 0L,
  step_size = 320L
)
mix_param <- list(
  est_method = "ASA", # changed method type: ASA, UD
  start_crit = 500L, # Bisection 3 Times
  start_step = 100L, # ASA_c = 2*100
  stop_rev_times = 3L,
  UseMidrunEst = TRUE 
) 
phi_vec <- c(.phi*10, .phi, .phi*0.1)
names(phi_vec) <- c("large", "medium", "small")
```


## Directories

```{r dir_params}
dir_name <- "./ASA_simulation_RDS"
pic_path <- "./figs"
```

## Cleaning and Plotting Functions

```{r cleaning_func}
extract_est <- function(df_list, has_early_stop=TRUE){
  util.levels <- c(paste0("x", 6:1, "neg"),
                        "x0",
                        paste0("x", 1:6, "pos"))
  # function
  FindSubList <- function(df, has_early_stop){
    if (has_early_stop){
      # Separate to 3 columns
      df <- df %>%
        separate_wider_delim(
          method_type,
          delim = "_early",
          names = c("method", "early_stop")
          )
    } else {
      df <- df %>% 
        rename(method = method_type)
    }
    df %>% 
      select(method, Nsim, any_of("early_stop"),
             matches("^x[1-9](pos|neg)_est")) %>% 
      add_column(x0 = 0L, .after = 1) %>% 
      rename_with(\(x) str_remove(x, "_est")) %>% 
      select(method, Nsim, any_of("early_stop"), !!!syms(util.levels))
  }
  newlist <- map(df_list,
                 \(x) FindSubList(x, has_early_stop=has_early_stop))
  newlist
}

# pivot longer and change 
utility_longer <- function(df){
  
  util.levels <- c(paste0("x", 6:1, "neg"),
                        "x0",
                        paste0("x", 1:6, "pos"))
  # pivot_longer to x and utility levels
  new_df <- df %>% 
    pivot_longer(cols = starts_with("x"), 
                 names_to = "utility", 
                 values_to = "x_value") %>% 
    mutate(utility =
             factor(utility,
                    labels = -6:6,
                    levels = util.levels
                    )
           )
  new_df
}

# saving pics
save_fig <- function(pname, p_path = pic_path,
                     width = 13, height = 8) {
  
  if (!file.exists(file.path(p_path, pname))) {
    ggsave(filename = pname,
           width = width,
           height = height,
           units = "in",
           device = "pdf",
           path = p_path)
  } else {
    cat("File already exists. Not saving:", file.path(pic_path, pname), "\n")
  }
}


# fig labels

latex_labels <- c(
  expression(x[6]^"-"), expression(x[5]^"-"), expression(x[4]^"-"),
  expression(x[3]^"-"), expression(x[2]^"-"), expression(x[1]^"-"),
  expression(x[1]^"+"), expression(x[2]^"+"), expression(x[3]^"+"),
  expression(x[4]^"+"), expression(x[5]^"+"), expression(x[6]^"+")
)
```


## True Value

Code: find true parameters.
```{r, true_val}
true_est <- find_optimal_params(params = param,
                          exp_params_init = exp_param$init_values,
                          x_num = exp_param$n_est) %>% 
  as_tibble_row()

# get ture x values
true_est.long <- true_est %>%
  pivot_longer(matches('x[0-9]'),
               values_to = 'true_x',
               names_to = 'utility') %>% 
  mutate(
    utility =
      factor(utility,
             labels = -6:6,
             levels = c(
                        paste0("x", 6:1, "neg"),
                        "x0",
                        paste0("x", 1:6, "pos"))
             )
    ) %>% 
  select(-c(L, L_2, G_2, lambda_KW))

# get true lambda
LA_df <- true_est %>%
  pivot_longer(cols = matches(".*[1-9][pos|neg]"),
               names_to = c("trial", "type"),
               names_pattern = "x(\\d)(.*)",
               values_to = "value") %>%
  mutate(
    trial = as.integer(trial),
    type = ifelse(type == "pos", "gain", "loss")  # Assign gain/loss
  ) %>% 
  pivot_wider(names_from = type, values_from = value)

true.KT_reg <- LA_df %>% 
  lm(gain ~ 0 + abs(loss), data = .) %>% 
  broom::tidy(conf.int = TRUE, conf.level = 0.95) %>% 
  pull(estimate)


get_minusx_utility <- function(x, data, method = c("interpolation", "power_func"), 
                               alpha = NULL, beta = NULL){
  method <- match.arg(method)
  
  minusx <- - x
  if (method == "interpolation") {
    interpolate_point <- approx(x = sort(c(data$loss, 0, data$gain)), y = -6:6, xout = minusx)
    minusx_utility <- interpolate_point$y
  } else { # method == "power_func"
    minusx_utility <- NA
  }
  
  return(minusx_utility)
}


KT <- function(data, output = c("coefficient", "classification", "all"),
               type = c("median", "mean")){
  output <- match.arg(output)
  type <- match.arg(type)
  
  gain_max <- max(data$gain)
  loss_min <- min(data$loss)
  
  lambda <- data %>% 
    pivot_longer(cols = c(gain, loss), names_to = "domain", values_to = 'x') %>% 
    mutate(utility = (-1)^(domain == "loss") * trial,
           minusx_utility = map_dbl(x, ~ get_minusx_utility(., data)),
           utility_ratio = pmap_dbl(list(domain, utility, minusx_utility), 
                                    ~ switch(..1, 
                                             gain = abs(..3 / ..2),
                                             loss = abs(..2 / ..3)))) %>% 
    summarise(estimate = switch(type, 
                                median = median(utility_ratio, na.rm = TRUE),
                                mean = mean(utility_ratio, na.rm = TRUE)),
              n_reasonable_points = sum(!is.na(utility_ratio)),
              criterion = ceiling(n_reasonable_points / 2),
              n_ratio_greater_1 = sum(utility_ratio > 1, na.rm = TRUE),
              n_ratio_less_1 = sum(utility_ratio < 1, na.rm = TRUE)) %>% 
    mutate(classification = case_when(n_ratio_greater_1 > criterion  ~ "averse",
                                      n_ratio_less_1 > criterion ~ "seeking",
                                      TRUE ~ "neutral"))
  
  if (output == "coefficient") {
    lambda$estimate
  } else if (output == "classification") {
    lambda$classification
  } else {
    lambda
  }
}

LA_df <- LA_df %>%
  nest(data = c(trial, gain, loss))%>% 
  mutate(
    KT_mean = map_dbl(data, \(x) KT(x, output = "coefficient", type= "mean")),
    KT_median = map_dbl(data, \(x) KT(x, output = "coefficient", type= "median"))
  )

true_lambda <- c("true_lambda.KW" = LA_df$lambda_KW,
                 "true_lambda.KT_mean" = LA_df$KT_mean,
                 "true_lambda.KT_median" = LA_df$KT_median,
                 "true_lambda.KT_reg" = true.KT_reg)
```


# Simulation 1 (new version)

```{r bound, eval=FALSE, include=FALSE}
file_name <- "boundary_parallel.RDS"
fname <- file.path(dir_name, file_name)
target_list <- read_rds(fname) %>% 
  extract_est(has_early_stop = FALSE)
```



```{r bound2}
file_name <- "boundary_lambda_vary.RDS"
fname <- file.path(dir_name, file_name)
bound_df <- read_rds(fname) %>% 
  rename(method = method_type) %>% 
  select(phi, method, alpha:lambda, Nsim, any_of("early_stop"),
         matches("^x[1-9](pos|neg)_est")) %>% 
  rename_with(\(x) str_remove(x, "_est")) %>% 
  add_column(x0 = 0L, .before = "x1pos")

# Add true value
bound_df <- bound_df %>%
  nest(data = !c(alpha:lambda)) %>%
  rowwise() %>%
  mutate(
    truev = list(
      find_optimal_params(
        params = list(
          "alpha" = alpha, "beta" = beta, "lambda" = lambda, "wp" = 0.5, "wn" = 0.5
          ),
        exp_params_init = exp_param$init_values,
        x_num = exp_param$n_est)
      )
    ) %>%
  ungroup() %>%
  unnest_wider(truev, names_sep = "_") %>%
  select(!matches("truev_(L(_2)?|G_2|lambda_KW)$")) # L, L2 G2 orlambdaKW

# unnest and pivot_longer
true_df <- bound_df %>%
  add_column(truev_x0 = 0) %>% 
  pivot_longer(
    cols = starts_with("truev"), 
    names_to = "utility",
    values_to = "true_value") %>% 
  mutate(utility = utility |>
           str_remove("^truev_")|>
           factor(labels = -6:6,
                  levels =
                    c(paste0("x", 6:1, "neg"),
                      "x0",
                      paste0("x", 1:6, "pos")))
         ) %>% 
  select(!data)

cleaned_df <- bound_df %>%
  select(alpha:data) %>% 
  unnest() %>%
  utility_longer() %>% 
  left_join(true_df, by = join_by(alpha, beta, lambda, utility))

rm(bound_df)
```

## Utility Curve Plots {.tabset}

顏色線段代表 95% 的觀測值分布範圍長度。黑色虛線為實際數值

```{r, fig.height=6.5, fig.width=12}
cleaned_df %>% 
  filter(lambda == 2.25 & phi != "small") %>%
  # filter(lambda == 2.25 ) %>%
  group_by(phi) %>% 
  ggplot(aes(y = utility)) +
  geom_hline(
    yintercept = 
      as.numeric(
        factor("x0",
               levels =
                 c(paste0("x", 6:1, "neg"),
                   "x0",
                   paste0("x", 1:6, "pos")))),
    color = "red2",
    linetype = "dashed", alpha = 0.8) +
  # True utility curve
  geom_line(
    aes(y = utility, x = true_value, group = 1),
    color = "black", linetype = "3331") +
  geom_point(
    aes(y = utility, x = true_value, group = 1),
    color = "black", pch = 1, size =2.5) +
  # 95% range
  stat_summary(
    aes(y = utility, x = x_value, color = phi, shape = phi),
    geom = "pointrange",
    fun = \(x) mean(x, na.rm = TRUE),
    fun.min = \(x) quantile(x, .025, na.rm = TRUE),
    fun.max = \(x) quantile(x, .975, na.rm = TRUE),
    position = position_dodge(width = 0.9),
    linewidth = 1.1, size = 0.6, alpha=.8
  ) +
  labs(x = "Elicited x ", y = "Values", color = "phi") +
  facet_wrap(~ method, dir="v", ncol=5, nrow=2) +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = 16),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14),
    legend.text = element_text(size = 15)) +
  ggtitle(glue("Value Curve"))

pname <- "study1_utility_curve.pdf"

if (!file.exists(file.path(pic_path, pname))) {
  ggsave(filename = pname,
         width = 12,
         height = 6.5,
         units = "in",
         device = "pdf",
         path = pic_path)
} else {
  cat("File already exists. Not saving:", file.path(pic_path, pname), "\n")
}
```

## Bias and RMSE


```{r summ_biasRMSE}
df.bias_RMSE <- cleaned_df %>%
  filter(utility != 0) %>% 
  mutate(
    boundary_type = ifelse(
        grepl(".*_fixbnd$", method),
        "fix_bnd",
        ifelse(
          grepl(".*_randInit$", method),
          "rand_init",
          "equal_exp")
        ),
    method = str_replace(method, "_(randInit|fixbnd)$", "")
  ) %>% 
  group_by(phi, method, boundary_type, utility, lambda) %>% 
  summarise(
   bias = mean(x_value - true_value)|> round(),
   RMSE = 
     (x_value - true_value)^2 |> 
     mean() |>
     sqrt() |>
     round(),
   .groups = "drop"
   )
```



```{r bias_bnd, fig.height=7, fig.width=13}
df.bias_RMSE %>% 
  filter(lambda == 2.25) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = bias,
    color = boundary_type,
    group = boundary_type),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = 0, color = "grey30", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = bias,
      color = boundary_type,
      shape = boundary_type),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_color_discrete(
    # values = c("fix_bnd" = "cyan4", "equal_exp" = "orange2"),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variants") +
  scale_shape_manual(
    values = c("fix_bnd" = 16, "equal_exp" = 17, "rand_init" = 15),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variants") +
  labs(x = "x_i",
       y = "Bias",
       title = "Bias")+
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14),
    legend.text = element_text(size = 15)
    )

pname <- "study1_bias.pdf"

if (!file.exists(file.path(pic_path, pname))) {
  ggsave(filename = pname,
         width = 13,
         height = 7,
         units = "in",
         device = "pdf",
         path = pic_path)
} else {
  cat("File already exists. Not saving:", file.path(pic_path, pname), "\n")
}
```

## RMSE

```{r RMSE_bnd, fig.height=7, fig.width=13}
df.bias_RMSE %>% 
  filter(lambda == 2.25) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = RMSE,
    color = boundary_type,
    group = boundary_type),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  # geom_hline(yintercept = c(500,-500), color = "red2", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = RMSE,
      color = boundary_type,
      shape = boundary_type),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_color_discrete(
    # values = c("fix_bnd" = "cyan4", "equal_exp" = "orange2"),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variants") +
  scale_shape_manual(
    values = c("fix_bnd" = 16, "equal_exp" = 17, "rand_init" = 15),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variants") +
  labs(x = "x_i",
       y = "RMSE",
       title = "RMSE")+
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14),
    legend.text = element_text(size = 15)
    )

pname <- "study1_RMSE.pdf"

if (!file.exists(file.path(pic_path, pname))) {
  ggsave(filename = pname,
         width = 13,
         height = 7,
         units = "in",
         device = "pdf",
         path = pic_path)
} else {
  cat("File already exists. Not saving:", file.path(pic_path, pname), "\n")
}

```

## Step Count

```{r eval=FALSE, include=FALSE}
len_df <- read_rds(fname) %>% 
  select(alpha:Nsim, ends_with("len")) %>%
  mutate(
    method = str_replace(method_type, "_(randInit|fixbnd)$", ""),
    variant = ifelse(
        grepl(".*_fixbnd$", method_type),
        "fix_bnd",
        ifelse(
          grepl(".*_randInit$", method_type),
          "rand_init",
          "equal_exp")
        ),
    .after = phi,
    .keep = "unused"
  )

len_df %>% 
  group_by(phi, lambda,  method, variant) %>% 
  filter(lambda ==2.25) %>% 
  mutate(
    mean_each_step = rowMeans(across(ends_with("len"))),
    # Q3_step_mean = rowMeans(across(ends_with("Q3")))
    .keep = "unused"
  ) %>%
  summarise(
    mean_step = mean(mean_each_step) |> round(),
    # Q3_mean_step = quantile(mean_each_step, .75)|> round(),
    .groups = "drop"
  ) %>% 
  select(!lambda) %>% 
  write_csv(
    file = file.path(pic_path, "step.csv")
  )

```



# Simulation 2

Read file
```{r read_mixture}
file_name <- "Bisection_mixASA_early_stop.RDS"

fname <- file.path(dir_name, file_name)
target_list <- read_rds(fname) %>% 
  extract_est()
```


```{r summ_table, paged.print=TRUE}
.tmp <- target_list %>%
  bind_rows(.id="phi") %>%
  select(-x0) %>% 
  utility_longer() %>%
  group_by(phi, method, early_stop, utility) %>% 
  summarise(variance = var(x_value)|> round(),
            upper_95 = quantile(x_value, .975)|> round(),
            lower_95 = quantile(x_value, .025)|> round(),
            mean = mean(x_value)|> round(),
            median = median(x_value) |> round(),
            .groups = "drop"
            ) 
# add true value to compute bias
.tmp <- .tmp %>% 
  mutate(method = str_remove(method, "Bisection_mixASA_")) %>% 
  full_join(true_est.long, by = join_by(utility)) %>% 
  mutate(mdn_bias = median - true_x,
         mean_bias = mean - true_x,
         early_stop = as.numeric(early_stop),
         RMSE = sqrt(mean_bias^2 + variance),
         .before = variance) %>%
  relocate(utility, early_stop, .after = phi) %>% 
  arrange(phi, utility, early_stop, RMSE)
```

## Bias (Mean)

-   Reference Line: 100, -100.

-   Some extreme values were truncated.

-   `ASA` 至少iteration 要10以上 bias 才比較小(不考慮phi_small)
  -   `ASA` (iteration =10) Bias 跟 Simulation 1.2 結果比似乎比較低(再確認)
  
  
```{r eval=FALSE, include=FALSE}
.tmp %>% 
  filter(early_stop == 10 & grepl("ASA", method) & phi !="small" )
```
 

 
  
```{r bias_early_stop, fig.height=6, fig.width=18}
.tmp %>% 
  filter(early_stop != 15) %>% 
  mutate(early_stop = as.factor(early_stop)) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = mean_bias,
    color = early_stop,
    group = early_stop),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = 0, color = "grey20", lty=2, alpha=0.8)+
  # geom_hline(yintercept = c(-200, 200), color = "red2", lty=3)+
  geom_point(
    aes(
      y = mean_bias,
      color = early_stop,
      shape = early_stop),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_shape_manual(
    values = c("5" = 16, "10" = 17)) +
  labs(x = "x_i",
       y = "Bias",
       color = "Itertation Number",
       shape = "Itertation Number",
       title = "Bias (Fixed Iteration)")+
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 17),
    legend.text = element_text(size = 15),
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14)
    )

pname <- "study2_bias.pdf"

if (!file.exists(file.path(pic_path, pname))) {
  ggsave(filename = pname,
         width = 18,
         height = 6,
         units = "in",
         device = "pdf",
         path = pic_path)
} else {
  cat("File already exists. Not saving:", file.path(pic_path, pname), "\n")
}
```

 
## RMSE

-   Reference Line: 500.

-   Some extreme values were truncated.

-   phi_medium時，`ASA(iteration=10)` SD 比 `Bisection` 小一點

-   `Bisection-Slier` Iteration 越多反而 SD 大
    
    -   表現特別好可能是模擬設定導致。

```{r sd_early_stop, fig.height=6, fig.width=18}
max_values <- .tmp %>%
  filter(method == "ASA") %>%
  group_by(phi,early_stop) %>% 
  summarise(max_rmse = max(RMSE, na.rm = TRUE), .groups = "drop") %>% 
  pivot_wider(names_from = early_stop,
              names_glue = "max_rmse_{early_stop}",
              values_from = max_rmse)
.tmp %>% 
  filter(early_stop != 15) %>% 
  mutate(early_stop = as.factor(early_stop)) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = RMSE,
    color = early_stop,
    group = early_stop),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = 0, color = "grey20", lty=2, alpha=0.8)+
  # geom_hline(aes(yintercept = max_rmse_10),
  #            color = "darkgreen", lty=2, alpha=0.6,
  #            size=1.1)+
  geom_point(
    aes(
      y = RMSE,
      color = early_stop,
      shape = early_stop),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_shape_manual(
    values = c("5" = 16, "10" = 17)) +
  labs(x = "x_i",
       y = "RMSE",
       color = "Itertation Number",
       shape = "Itertation Number",
       title = "RMSE (Fixed Iteration)")+
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 17),
    legend.text = element_text(size = 15),
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14)
    )

pname <- "study2_RMSE.pdf"

if (!file.exists(file.path(pic_path, pname))) {
  ggsave(filename = pname,
         width = 18,
         height = 6,
         units = "in",
         device = "pdf",
         path = pic_path)
} else {
  cat("File already exists. Not saving:", file.path(pic_path, pname), "\n")
}
```
```{r include=FALSE}
rm(max_values)
```


### Relative RMSE

```{r fig.height=6, fig.width=16}
.tmp %>% 
  filter(early_stop != 15) %>% 
  group_by(phi, utility, early_stop) %>%
  mutate(
    relative_RMSE = RMSE / RMSE[method == "Bisection"],
    early_stop = as.factor(early_stop)
  ) %>% 
  filter(method != "Bisection") %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = relative_RMSE,
    color = early_stop,
    group = early_stop),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = 1, color = "grey20", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = relative_RMSE,
      color = early_stop,
      shape = early_stop),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_shape_manual(
    values = c("5" = 16, "10" = 17)) +
  labs(x = "x_i",
       y = "relative RMSE",
       color = "Itertation Number",
       shape = "Itertation Number",
       title = "Relative RMSE to Bisection (Fixed Iteration)")+
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14),
    legend.text = element_text(size = 15)
    )
  
pname <- "study2_relativeRMSE.pdf"

if (!file.exists(file.path(pic_path, pname))) {
  ggsave(filename = pname,
         width = 16,
         height = 6,
         units = "in",
         device = "pdf",
         path = pic_path)
} else {
  cat("File already exists. Not saving:", file.path(pic_path, pname), "\n")
}
```



## Loss Aversion {.tabset}

```{r KT_reg}
# data format: data.frame with 3 columns
# trial: 1, ..., 6
# gain: x1+, ..., x6+
# loss: x1-, ..., x6-

# KT_reg <- function(data, output = c("coefficient", "classification", "all")){
#   output <- match.arg(output)
#   
#   lambda <- data %>% 
#     lm(gain ~ 0 + abs(loss), data = .) %>% 
#     broom::tidy(conf.int = TRUE, conf.level = 0.95) %>% 
#     mutate(classification = case_when(conf.low > 1 ~ "averse",
#                                       conf.high < 1 ~ "seeking",
#                                       TRUE ~ "neutral"))
#    
#   if (output == "coefficient") {
#     lambda$estimate
#   } else if (output == "classification") {
#     lambda$classification
#   } else {
#     lambda
#   }
# }


KT_reg_fast <- function(data, output) {
  x <- abs(data$loss)
  y <- data$gain
  if (anyNA(x)) stop("x problem")
  else if (anyNA(y)) stop("y problem")
  else if (any(x %in% c(-Inf, Inf))) stop("x inf")
  else if (any(y %in% c(-Inf, Inf))) stop("y inf")
  coef <- sum(x * y) / sum(x^2)  # Slope estimate for gain ~ 0 + abs(loss)
  
  if (output == "coefficient") {
    coef
  }
}
# for KT, see Simulation Setting code part

```


```{r LA_est}
file_path <- file.path(dir_name, "LA_reslut_df.RDS")

if (file.exists(file_path)) {
  LA_result <- read_rds(file_path)
  print(paste("File read from:", file_path))
} else {
  library(furrr)
  # clean data type and create KW
  LA_result <- target_list %>%
    bind_rows(.id="phi") %>%
    select(phi:early_stop, matches(".*[1-9][pos|neg]")) %>% 
    mutate(KW = -x1pos/x1neg)
  
  LA_result <- LA_result %>% 
    pivot_longer(cols = matches(".*[1-9][pos|neg]"),
                   names_to = c("trial", "type"),
                   names_pattern = "x(\\d)(.*)",
                   values_to = "value") %>%
    mutate(
      trial = as.integer(trial),
      type = ifelse(type == "pos", "gain", "loss")  # Assign gain/loss
    ) %>% 
    pivot_wider(names_from = type, values_from = value) %>%
    unnest(c(gain, loss)) %>% 
    nest(data = c(trial, gain, loss))
  
  plan(multisession)
  # Measure system time for paralleled processing
  tm <- system.time({
    LA_result <- LA_result %>%
      mutate(
        early_stop = as.integer(early_stop),
        KT_mean = future_map_dbl(data, ~ KT(.x, output = "coefficient", type = "mean")),
        KT_median = future_map_dbl(data, ~ KT(.x, output = "coefficient", type = "median")),
        KT_reg = future_map_dbl(data, ~ KT_reg_fast(., output = "coefficient"))
      )
  })
  cat("Time taken: \n\n")
  print(tm)
  # Save LA_result as an RDS file
  saveRDS(LA_result, file = file_path)
  print(paste("File saved at:", file_path))
}
```

### Extreme Value Count

小於0 或者 無限大

```{r ext_LA, paged.print=TRUE}
LA_result %>% 
  group_by(phi, method, early_stop) %>% 
  summarise(extreme_KW = sum(KW<0) + sum(KW==Inf),
            extreme_KT_mean = (sum(KT_mean<0, na.rm = T) +
              sum(KT_mean==Inf, na.rm = T) +
              sum(is.na(KT_mean))),
            extreme_KT_median = (sum(KT_median<0, na.rm = T) +
              sum(KT_median==Inf, na.rm = T) +
              sum(is.na(KT_median))),
            extreme_KT_reg = (sum(KT_reg<0, na.rm = T) +
              sum(KT_reg==Inf, na.rm = T) +
              sum(is.na(KT_reg))),
            .groups = "drop"
            ) %>% 
  kable("html", align="c") %>% 
  kable_styling(bootstrap_options = c("striped", "hover")) %>% 
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2) %>% 
  scroll_box(height = "500px", width = "800px")
```

### Loss Aversion Results{.tabset .tabset-fade .tabset-pills}

```{r include=FALSE}
LA_result <- LA_result %>% 
  filter(early_stop!=15)
```
@abdellaouiMeasuring2016 的重點分析之一，參考過去子堯分析的code參考來使用。目前有兩種係數估計。

-   @kobberlingIndex2005 下估計量: $\lambda_{KW} = \frac{-x_1^+}{x_1^-}$
    
    * 只考慮$x_1^+$和$x_1^-$。

-   @kahnemanProspect1979 下估計量1: $\frac{U(x_i^+)}{U(x_i^+)}$
    
    * 待補

-  @kahnemanProspect1979 下估計量2: Regress $x_i^+$  on $x_i^-$ without intercept terms.

True Values are respectively: `r true_lambda`.


```{r}
LA_result <- LA_result %>%
  pivot_longer(matches("^(KT|KW)"),
               names_to = "LA_type",
               values_to = "LA_est") %>% 
  # add_column(true_lambda)
  nest(tmp = !LA_type) %>% 
  add_column(true_lambda) %>% 
  unnest(tmp)
 
```



#### 95% CI

```{r fig.height=10, fig.width=15}
LA_result %>%
  filter(is.finite(LA_est) & LA_type != "KT_reg") %>%
  mutate(early_stop = factor(early_stop)) %>% 
  group_by(phi, method, LA_type, early_stop) %>% 
  ggplot() +
  geom_vline(
    aes(xintercept = true_lambda),
    lty=2, color = "grey30", linewidth =1.05
    ) +
  stat_summary(
    aes(x = LA_est, y = method, color = early_stop),
    geom = "errorbar",
    position = position_dodge(0.6),
    fun.min = function(x) quantile(x, 0.025, na.rm = TRUE),
    fun.max = function(x) quantile(x, 0.975, na.rm = TRUE),
    linewidth = 1.2
  ) +
  stat_summary(
    aes(x = LA_est, y = method, color = early_stop, shape = early_stop),
    position = position_dodge(0.6),
    fun = mean,
    geom = "point",
    size = 3.5,
  ) +
  # xlim(0, 6) +
  facet_grid(phi ~ LA_type,
             # labeller = "label_both"
             scales = "free"
            ) +
  labs(x = "Loss Aversion Coefficient",
   y = "Methods",
   color = "Itertation Number",
   shape = "Itertation Number",
   title = "Loss Aversion Coefficients Estimates") +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 17),
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14)
    )

pname <- "study2_LA_Summary.pdf"
save_fig(pname, width = 11, height = 8)
```



```{r biasRMSE}
LA_summ <- LA_result %>%
  group_by(phi, LA_type, early_stop, method) %>% 
  summarise(
    bias = mean(LA_est - true_lambda, na.rm = TRUE),
    RMSE = mean((LA_est - true_lambda)^2, na.rm = TRUE) |>
      sqrt(),
    .groups = "drop"
  ) %>% 
  group_by(phi, LA_type, early_stop) %>% 
  mutate(relative_RMSE = RMSE / RMSE[method == "Bisection"]) %>% 
  ungroup()
```

#### Bias

MOBS 和 PEST 有時會產生 `NA` / `Inf` 的值，導致無法計算平均、RMSE，因此闕漏。

```{r, fig.height=8, fig.width=13}
LA_summ  %>% 
  filter(is.finite(bias) & LA_type != "KT_reg") %>% 
  mutate(early_stop = as.factor(early_stop)) %>%
  ggplot(aes(x = method)) +
  geom_hline(yintercept = 0, color = "grey30", lty = 2, alpha = 0.8) +
  geom_point(aes(y = bias,
               shape = early_stop,
               color = early_stop,
               group = early_stop),
             position = position_dodge(width = 0.4),
             size = 3.0) +
  facet_grid(rows = vars(phi),
             cols = vars(LA_type),
             scales = "free_y"
             ) +
  labs(x = "Method",
       y = "Bias",
       color = "Itertation Number",
       shape = "Itertation Number",
       title = "Loss Aversion Coefficients: Bias")+
  theme(legend.position = "bottom",
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        axis.text.x = element_text(size = 11, angle = 90, vjust = .55),
        strip.text= element_text(size = 13),
        title = element_text(size = 18))

pname <- "study2_LA_bias.pdf"
save_fig(pname, width = 11, height = 8)
```


#### RMSE

```{r, fig.height=8, fig.width=13}
LA_summ  %>% 
  filter(is.finite(RMSE) & LA_type != "KT_reg") %>% 
  mutate(early_stop = as.factor(early_stop)) %>%
  ggplot(aes(x = method)) +
  geom_hline(yintercept = 0, color = "grey30", lty = 2, alpha = 0.8) +
  geom_point(aes(y = RMSE,
               shape = early_stop,
               color = early_stop),
             position = position_dodge(width = 0.5),
             size = 3.0) +
  facet_grid(rows = vars(phi),
             cols = vars(LA_type),
             scales = "free_y"
             ) +
  labs(x = "Method",
       y = "RMSE",
       color = "Itertation Number",
       shape = "Itertation Number",
       title = "Loss Aversion Coefficients: RMSE")+
  theme(legend.position = "bottom",
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        axis.text.x = element_text(size = 11, angle = 90, vjust = .55),
        strip.text= element_text(size = 13),
        title = element_text(size = 18))

pname <- "study2_LA_RMSE.pdf"
save_fig(pname, width = 11, height = 8)
```

#### Relative RMSE

因為單看RMSE可能看不太出實際狀況，這裡也呈現relative RMSE，計算方式是以 Bisection 的RMSE作為分母，因此若小於1 代表比Bisection法更具efficiency.

```{r, fig.height=8, fig.width=13}
LA_summ  %>% 
  filter(is.finite(relative_RMSE) & LA_type != "KT_reg") %>% 
  filter(!method %in% c("Bisection", "MOBS", "PEST", "PEST_randInit")) %>%
  mutate(early_stop = as.factor(early_stop)) %>%
  ggplot(aes(x = method)) +
  geom_point(aes(y = relative_RMSE,
               shape = early_stop,
               color = early_stop),
             position = position_dodge(width = 0.5),
             size = 3.0) +
  geom_hline(yintercept = 1, color = "grey30", lty = 2, alpha = 0.8) +
  # geom_line(aes(y = RMSE,
  #               group = early_stop,
  #              color = early_stop),
  #           linewidth = 1.2,
  #           alpha = 0.8)+
  facet_grid(rows = vars(phi),
             cols = vars(LA_type),
             scales = "free_y"
             ) +
  labs(x = "Method",
       y = "Relative RMSE",
       color = "Itertation Number",
       shape = "Itertation Number",
       title = "Loss Aversion Coefficients: Relative RMSE to Bisection")+
  theme(legend.position = "bottom",
        axis.text.x = element_text(size = 12, angle = 90, vjust = .55),
        legend.title = element_text(size = 16),
        strip.text= element_text(size = 13),
        legend.text = element_text(size = 14),
        title = element_text(size = 18))

pname <- "study2_LA_relativeRMSE.pdf"
save_fig(pname, width = 11, height = 8)

```

### Iteration = 10 only

#### 95% CI

```{r fig.height=8, fig.width=11}
LA_result %>%
  mutate(early_stop = factor(early_stop)) %>% 
  # filter(!grepl("(PEST|MOBS)", method)) %>%
  filter(is.finite(LA_est) & early_stop == 10 & LA_type != "KT_reg") %>%
  group_by(phi, method, LA_type, early_stop) %>% 
  ggplot() +
  geom_vline(
    aes(xintercept = true_lambda),
    lty=2, color = "grey30", linewidth =1.05
    ) +
  stat_summary(
    aes(x = LA_est, y = method),
    geom = "errorbar",
    position = position_dodge(0.6),
    fun.min = \(x) quantile(x, 0.025, na.rm = TRUE),
    fun.max = \(x) quantile(x, 0.975, na.rm = TRUE),
    color = "cyan3",
    linewidth = 1.2, width = 0.5
  ) +
  stat_summary(
    aes(x = LA_est, y = method),
    position = position_dodge(0.6),
    fun = \(x) mean(x, na.rm = TRUE),
    geom = "point",
    color = "cyan4",
    shape = 17,
    size = 3.5,
  ) +
  facet_grid(phi ~ LA_type,
           # labeller = "label_both"
           scales = "free"
          ) +
  labs(x = "Loss Aversion Coefficient",
   y = "Methods",
   title = "Loss Aversion Coefficients Estimates (Iteration = 10)") +
  theme(
    # legend.position = "bottom",
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14)
    )

pname <- "study2_LA_Summary_iter10.pdf"
save_fig(pname, width = 11, height = 8)
```

#### Bias

maybe useful:

https://teunbrand.github.io/ggh4x/reference/facetted_pos_scales.html

```{r, fig.height=8, fig.width=10}
LA_summ  %>% 
  filter(is.finite(bias) & early_stop == 10 & LA_type != "KT_reg") %>%
  mutate(early_stop = as.factor(early_stop)) %>%
  ggplot(aes(x = method)) +
  geom_hline(yintercept = 0, color = "grey30", lty = 2, alpha = 0.8) +
  geom_point(aes(y = bias),
             position = position_dodge(width = 0.4),
             color = "cyan4",
             shape = 17,
             size = 3.0) +
  facet_grid(rows = vars(phi),
             cols = vars(LA_type),
             # scales = "free_y"
             ) +
  labs(x = "Method",
       y = "Bias",
       title = "Loss Aversion Coefficients: Bias")+
  theme(axis.text.x = element_text(size = 11, angle = 90, vjust = .55),
        strip.text= element_text(size = 13),
        title = element_text(size = 18))

pname <- "study2_LA_bias_iter10.pdf"
save_fig(pname, width = 10, height = 8) # width = 10 may be better
```

#### RMSE

```{r, fig.height=8, fig.width=10}
LA_summ  %>% 
  filter(is.finite(RMSE) & early_stop == 10 & LA_type != "KT_reg") %>%
  mutate(early_stop = as.factor(early_stop)) %>%
  ggplot(aes(x = method)) +
  geom_hline(yintercept = 0, color = "grey30", lty = 2, alpha = 0.8) +
  geom_point(aes(y = RMSE),
             position = position_dodge(width = 0.4),
             color = "cyan4",
             shape = 17,
             size = 3.0) +
  facet_grid(rows = vars(phi),
             cols = vars(LA_type),
             scales = "free_y"
             ) +
  labs(x = "Method",
       y = "RMSE",
       title = "Loss Aversion Coefficients: RMSE")+
  theme(axis.text.x = element_text(size = 11, angle = 90, vjust = .55),
        strip.text= element_text(size = 13),
        title = element_text(size = 18))

pname <- "study2_LA_RMSE_iter10.pdf"

save_fig(pname, width = 10, height = 8)
```

#### relative RMSE

```{r, fig.height=8, fig.width=10}
LA_summ  %>% 
  filter(is.finite(relative_RMSE) & early_stop == 10 & LA_type != "KT_reg") %>% 
  filter(!method %in% c("Bisection", "MOBS", "PEST", "PEST_randInit")) %>%
  mutate(early_stop = as.factor(early_stop)) %>%
  ggplot(aes(x = method)) +
  geom_point(aes(y = relative_RMSE),
             color = "cyan4",
             shape = 17,
             position = position_dodge(width = 0.5),
             size = 3.0) +
  geom_hline(yintercept = 1, color = "grey30", lty = 2, alpha = 0.8) +
  facet_grid(rows = vars(phi),
             cols = vars(LA_type),
             scales = "free_y"
             ) +
  labs(x = "Method",
       y = "Relative RMSE",
       title = "Loss Aversion Coefficients: Relative RMSE to Bisection")+
  theme(axis.text.x = element_text(size = 12, angle = 90, vjust = .55),
        strip.text= element_text(size = 13),
        title = element_text(size = 18))

pname <- "study2_LA_relativeRMSE_iter10.pdf"

save_fig(pname, width = 10, height = 8)
```





## Monotonicity

When $\phi$ is small (0.00367), at this level about $1/3$ observations of ASA violated monotonicity.

Since the boundary selection in Bisection-based methods have assumed monotonicity, there's no violations in these methods.

```{r monotone, paged.print=TRUE, rows.print=10}
monotone_df <- target_list %>% 
  bind_rows(.id = "phi") %>% 
  # mutate(phi = phi_vec[sub("phi_","", phi,)]) %>% 
  rowwise() %>%
  mutate(violation = is.unsorted(c(x6neg, x5neg,
                                   x4neg, x3neg,
                                   x2neg, x1neg, 
                                   x1pos, x2pos,
                                   x3pos, x4pos,
                                   x5pos, x6pos))) %>%
  ungroup()
monotone_df %>% 
  group_by(phi, method, early_stop) %>%
  summarise(violation_ratio = sum(violation)/1000, .groups = "drop") %>% 
  # ungroup() %>% 
  # filter(violation_count>0) %>%
  mutate(early_stop = as.numeric(early_stop)) %>% 
  arrange(phi, violation_ratio) %>% 
  kable("html", align="c") %>% 
  kable_styling(bootstrap_options = c("striped", "hover")) %>% 
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2) %>% 
  scroll_box(height = "500px")
```

-   Violation 共有7419筆， 計算 AUC 時會把這些剔除掉


## Curvature:

Normalizing utility curve (divided gains/losses b y$x_6^+/x_6^-$), use AUC $\geq \frac{1}{2}$ to classify convex/concave [@abdellaouiMeasuring2016]. 

- For gain domain, define utility curve as *concave* if `auc_pos` > 0.5.

- For loss domain, define utility curve as *convex* if `auc_neg` > 0.5.

- For nstrange observations (AUC>1 or AUC<0, some of them result from violation of monotonicity), they are labelled *Not Classified*

```{r AUC2}
# clean data type and normalizing
data_norm <- monotone_df %>%
  # filter(!violation) %>% 
  mutate(
    across(ends_with("pos"), \(x) x/x6pos),
    across(ends_with("neg"), \(x) -(x/x6neg))
  ) %>% 
  mutate(
      pos_vec = pmap(list(x1pos, x2pos, x3pos, x4pos, x5pos, x6pos), c),
      neg_vec = pmap(list(x1neg, x2neg, x3neg, x4neg, x5neg, x6neg), c),
      .keep = "unused"
  ) 

compute_auc <- function(x, y) {
  triangle_area <- (x[1] * y[1]) / 2
  trapezoidal_area <- sum((y[-1] + y[-length(y)]) * diff(x) / 2)

  triangle_area + trapezoidal_area
}

classify_curvature <- function(auc, domain = c("gain", "loss")) {
  domain = match.arg(domain)
  
  if (is.na(auc)) {
    return("Not Classified")
    stop("AUC value is missing (NA).")
  }
  if (auc > 1 | auc < 0) {
    return("Not Classified")
    stop("AUC value not normalized.")
  }
  
  if (auc == .5) {
    return("linear")
  } else if (domain == "gain") {
    return(ifelse(auc > 0.5,
                  "concave",
                  "convex"))
  } else if (domain == "loss") {
    return(ifelse(auc > 0.5,
                  "convex",
                  "concave"))
  }
}

data_norm <- data_norm %>%
  # Apply AUC calculation on the combined vectors
  mutate(
    auc_pos = map_dbl(pos_vec, ~ compute_auc(.x, 1:6 / 6)),
    auc_neg = map_dbl(neg_vec, ~ -compute_auc(.x, 1:6 / 6))
  ) %>% 
  # filter(!(is.na(auc_pos)|is.na(auc_neg))) %>% 
  mutate(
    pos_curv = map_chr(auc_pos, ~ classify_curvature(.x, "gain")),
    neg_curv = map_chr(auc_neg, ~ classify_curvature(.x, "loss"))
  )
```

```{r AUC_viz,fig.height=7, fig.width=18, rows.print=16}
contingency_df <- as.data.frame(
  with(data_norm, table(pos_curv, neg_curv, method, phi))
)

ggplot(contingency_df, aes(x = pos_curv, y = neg_curv, fill = Freq)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "grey95", high = "orange2") +
  facet_grid(phi~ method) +
  labs(title = "Curvature Classification (AUC)",
       x = "Positive Curvature",
       y = "Negative Curvature",
       fill = "Count") +
  theme_minimal()+
  theme(legend.position = "bottom",
        legend.text = element_text(size=11),
        strip.text = element_text(size=11),
        axis.text.x = element_text(size=11, angle = 45,hjust = 1))
```


# Simulation 3: Tuning Hyperpartameters

就 `Bisection_mixASA` 法裡面的幾個參數進行微調:

1. `Bisection` 的 step size 到達多少時切換成 `ASA` :

    - $300, 500, 1000$
    
2. `ASA` 一開始的step size:
    
    - $50, 100, 150$
    
Bisection_ASA (限定 trial 數下)

```{r read_hyp}
file_name <- "Mixture_hyp_param.RDS" 
fname <- file.path(dir_name, file_name)
target_list <- read_rds(fname) %>% 
  extract_est()
```


```{r eval=FALSE, include=FALSE}
# Step Size Analysis
get_last_step <- function(vec){
    step_size <- diff(vec)
    len <- length(step_size)
    step_size[len]
}

tmp.step <- read_rds(fname) %>%
  bind_rows(.id="phi") %>% 
  select(-(ends_with("est")|ends_with("len")|matches("^[LG]"))) %>% 
  mutate(across(x1pos:x6neg,
                \(x) map_int(x, get_last_step)),
         .keep= "unused") %>% 
  pivot_longer(cols = starts_with("x"), 
               names_to = "utility", 
               values_to = "x_value") %>% 
  mutate(utility =
           factor(utility,
                  labels = -6:6,
                  levels = c(paste0("x", 6:1, "neg"),
                      "x0",
                      paste0("x", 1:6, "pos"))
                  )
         )

tmp.step %>% 
  separate_wider_delim(
    method_type,
    delim = "_early",
    names = c("method", "early_stop")
  ) %>% 
  mutate(method = str_remove(method, "Bisection_mixASA_")) %>% 
  group_by(phi, method, early_stop, utility) %>% 
  summarise(sd = sd(x_value)|> round(),
            median = median(x_value) |> round(),
            upper_95 = quantile(x_value, .975)|> round(),
            lower_95 = quantile(x_value, .025)|> round(),
            # mean = mean(x_value)|> round(),
            .groups = "drop"
            ) 
```

```{r}
bound_df <- file.path(dir_name, "boundary_lambda_vary.RDS") %>% 
  read_rds() %>% 
  rename(method = method_type) %>% 
  select(phi, method, alpha:lambda, Nsim, any_of("early_stop"),
         matches("^x[1-9](pos|neg)_est")) %>% 
  rename_with(\(x) str_remove(x, "_est")) %>% 
  add_column(x0 = 0L, .before = "x1pos")

# Add true value
bound_df <- bound_df %>%
  nest(data = !c(alpha:lambda)) %>%
  rowwise() %>%
  mutate(
    truev = list(
      find_optimal_params(
        params = list(
          "alpha" = alpha, "beta" = beta, "lambda" = lambda, "wp" = 0.5, "wn" = 0.5
          ),
        exp_params_init = exp_param$init_values,
        x_num = exp_param$n_est)
      )
    ) %>%
  ungroup() %>%
  unnest_wider(truev, names_sep = "_") %>%
  select(!matches("truev_(L(_2)?|G_2|lambda_KW)$")) # L, L2 G2 orlambdaKW

# unnest and pivot_longer
true_df <- bound_df %>%
  add_column(truev_x0 = 0) %>% 
  pivot_longer(
    cols = starts_with("truev"), 
    names_to = "utility",
    values_to = "true_value") %>% 
  mutate(utility = utility |>
           str_remove("^truev_")|>
           factor(labels = -6:6,
                  levels =
                    c(paste0("x", 6:1, "neg"),
                      "x0",
                      paste0("x", 1:6, "pos")))
         ) %>% 
  select(!data)

cleaned_df <- bound_df %>%
  select(alpha:data) %>% 
  unnest() %>%
  utility_longer() %>% 
  left_join(true_df, by = join_by(alpha, beta, lambda, utility)) %>% 
  filter(lambda == 2.25 & grepl("(ASA.*|Bisection.*_fixbnd)", method))

```

```{r summaryMix}
# Extract bisection and ASA from Simulation3
early_stop_sim <- 
  read_rds(file.path(dir_name, "Bisection_mixASA_early_stop.RDS")) %>% 
  extract_est() %>% 
  bind_rows(.id = "phi") %>%
  filter(method %in% c("ASA", "ASA_randInit", "Bisection", "Bisection_Slider")) %>% 
  select(-x0) %>% 
  utility_longer() %>% 
  group_by(phi, method, early_stop, utility) %>% 
  summarise(variance = var(x_value)|> round(),
            upper_95 = quantile(x_value, .975)|> round(),
            lower_95 = quantile(x_value, .025)|> round(),
            mean = mean(x_value)|> round(),
            median = median(x_value) |> round(),
            .groups = "drop"
            ) 

early_stop_sim <- early_stop_sim %>% 
  full_join(true_est.long, by = join_by(utility)) %>% 
  mutate(mdn_bias = median - true_x,
         mean_bias = mean - true_x,
         early_stop = as.numeric(early_stop),
         RMSE = sqrt(mean_bias^2 + variance),
         .before = variance) %>%
  relocate(utility, early_stop, .after = phi) %>% 
  arrange(phi, utility, early_stop, RMSE)
.tmp <- target_list %>%
  bind_rows(.id="phi") %>%
  select(-x0) %>% 
  utility_longer() %>%
  group_by(phi, method, early_stop, utility) %>% 
  summarise(variance = var(x_value)|> round(),
            upper_95 = quantile(x_value, .975)|> round(),
            lower_95 = quantile(x_value, .025)|> round(),
            mean = mean(x_value)|> round(),
            median = median(x_value) |> round(),
            .groups = "drop"
            ) 
# add true value to compute bias
.tmp <- .tmp %>% 
  mutate(method = str_remove(method, "Bisection_mixASA_")) %>% 
  full_join(true_est.long, by = join_by(utility)) %>% 
  mutate(mdn_bias = median - true_x,
         mean_bias = mean - true_x,
         early_stop = as.numeric(early_stop),
         RMSE = sqrt(mean_bias^2 + variance),
         .before = variance) %>%
  bind_rows(early_stop_sim) %>% # bind simulation 3
  relocate(utility, early_stop, .after = phi) %>% 
  arrange(phi, utility, early_stop, RMSE)
```

```{r include=FALSE}
rm(early_stop_sim)
```

### Bias (Mean)


-   Reference Line: 500, -500.


```{r bias_hyp, fig.height=7, fig.width=22}
.tmp %>% 
  filter(early_stop != 15) %>% 
  mutate(early_stop = as.factor(early_stop)) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(x = utility, y = mean_bias,
                group = early_stop, color = early_stop),
             size = 1.05) +
  geom_hline(yintercept = c(500,-500), color = "red2", lty=2, alpha=0.8)+
  geom_point(aes(y = mean_bias, color = early_stop, shape = early_stop), size =3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             scales = "free_y") +
  # ylim(-1500, 1500)+
  labs(x = "x_i",
       y = "Bias",
       color = "Itertation Number",
       shape = "Itertation Number",
       title = "Bias (Fixed Iteration)")+
  theme(legend.position = "bottom",
        legend.title = element_text(size = 16),
        axis.text.x = element_text(size = 11),
        strip.text= element_text(size = 13),
        legend.text = element_text(size = 14),
        title = element_text(size = 18))
```

### RMSE

```{r RMSE_hyp, fig.height=7, fig.width=22}
max_values <- .tmp %>%
  filter(method == "ASA") %>%
  group_by(phi,early_stop) %>% 
  summarise(max_rmse = max(RMSE, na.rm = TRUE), .groups = "drop") %>% 
  pivot_wider(names_from = early_stop,
              names_glue = "max_rmse_{early_stop}",
              values_from = max_rmse)

.tmp %>% 
  filter(early_stop != 15) %>% 
  mutate(early_stop = as.factor(early_stop)) %>% 
  left_join(max_values, by = "phi") %>%
  ggplot(aes(x = utility)) +
  geom_line(aes(x = utility, y = RMSE,
                group = early_stop, color = early_stop),
            size = 1.05) +
  geom_hline(aes(yintercept = max_rmse_10),
             color = "darkgreen", lty=2, alpha=0.8,
             size=1.1)+
  geom_hline(yintercept = 500,
             color = "red4", linetype="3313", alpha=0.8)+
  geom_point(aes(y = RMSE, color = early_stop, shape = early_stop), size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             scales = "free_y") +
  # ylim(-50, 2500)+
  labs(x = "x_i",
       y = "RMSE",
       color = "Itertation Number",
       shape = "Itertation Number",
       title = "RMSE (Fixed Iteration)")+
  theme(legend.position = "bottom",
        legend.title = element_text(size = 16),
        axis.text.x = element_text(size = 11),
        strip.text= element_text(size = 13),
        legend.text = element_text(size = 14),
        title = element_text(size = 18))
```

### Relative RMSE

```{r rRMSE_hyp, fig.height=7, fig.width=22}
.tmp %>% 
  group_by(phi, utility, early_stop) %>% 
  mutate(early_stop = as.factor(early_stop),
         relative_RMSE = RMSE / RMSE[method == "Bisection"]) %>%
  filter(early_stop != 15 & method !="Bisection") %>% 
  ungroup() %>% 
  # left_join(max_values, by = "phi") %>%
  ggplot(aes(x = utility)) +
  geom_line(aes(x = utility, y = relative_RMSE,
                group = early_stop, color = early_stop),
            size = 1.05) +
  geom_hline(yintercept = 1,
             color = "grey20", lty=2, alpha=0.8)+
  geom_point(aes(y = relative_RMSE, color = early_stop, shape = early_stop), size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             scales = "free_y") +
  # ylim(-50, 2500)+
  labs(x = "x_i",
       y = "Relative RMSE",
       color = "Itertation Number",
       shape = "Itertation Number",
       title = "Relative RMSE to Bisection (Fixed Iteration)")+
  theme(legend.position = "bottom",
        legend.title = element_text(size = 16),
        axis.text.x = element_text(size = 11),
        strip.text= element_text(size = 13),
        legend.text = element_text(size = 14),
        title = element_text(size = 18))
```

---
# References



