---
title: "Bisection Simulation: Whole utility Curve"
author: "Wei-Chen Chang"
date: "`r Sys.Date()`"
output: 
  html_document:
     toc: true
     toc_depth: 2
     toc_float: true
     code-link: true
     code-tools: true
     code_folding: show
     code_download: true
     code-overflow: "scroll"
     self-contained: true
     number_sections: false
     df_print: paged
bibliography: "CPT_LA_new.bib"  
csl: "apa.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.align = "center",
	warning = FALSE,
	rows.print=11,
	paged.print=TRUE
)
```


```{r lib, message=FALSE, include=FALSE}
library(tidyverse)
library(DT)
library(glue)
library(magrittr)
library(patchwork)
library(kableExtra)
# import functions
source("../functions/player_and_lotteries.R")
# source("../functions/TO_exp.R")
# ggplot settings
theme_set({
  theme_bw()+    
  theme(axis.title = element_text(size = 16),
        # axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text = element_text(size = 13),
        strip.text= element_text(size = 12),
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        title = element_text(size = 18))
})
```


# Simulation Setting(Code Part)

```{r params}
# Simulation Parameters
Nsim <-  1000L
.phi <-  0.0367 # err = 1e-8, 0.027513126 is err = 1e-6
param <-  list("alpha"=.88, "beta"=.88, "lambda"=2.25, "wp"=.5, "wn"=.5)
exp_param <- list(
  init_values =
    list("G"= 2000L,
         "g"=300L, "l"=-300L, "x1+"=1000L),
  random_init = FALSE,
  fix_bnd_width = FALSE,
  n_est = 3L + (6*2L),
  min_step = 0L,
  step_size = 320L
)
mix_param <- list(
  est_method = "ASA", # changed method type: ASA, UD
  start_crit = 500L, # Bisection 3 Times
  start_step = 100L, # ASA_c = 2*100
  stop_rev_times = 3L,
  UseMidrunEst = TRUE 
) 
phi_vec <- c(.phi*10, .phi, .phi*0.1)
names(phi_vec) <- c("large", "medium", "small")
```


## Directories

```{r dir_params}
dir_name <- "./ASA_simulation_RDS"
pic_path <- "./figs"
```

## Cleaning and Plotting Functions

```{r cleaning_func}
# pivot longer and change 
utility_longer <- function(df){
  
  util.levels <- c(paste0("x", 6:1, "neg"),
                        "x0",
                        paste0("x", 1:6, "pos"))
  # pivot_longer to x and utility levels
  new_df <- df %>% 
    pivot_longer(cols = starts_with("x"), 
                 names_to = "utility", 
                 values_to = "x_value") %>% 
    mutate(utility =
             factor(utility,
                    labels = -6:6,
                    levels = util.levels
                    )
           )
  new_df
}

# saving pics
save_fig <- function(pname, p_path = pic_path,
                     width = 13, height = 8) {
  
  if (!file.exists(file.path(p_path, pname))) {
    ggsave(filename = pname,
           width = width,
           height = height,
           units = "in",
           device = "pdf",
           path = p_path)
  } else {
    cat("File already exists. Not saving:", file.path(pic_path, pname), "\n")
  }
}


# fig labels in math expression style
latex_labels <- c(
  expression(x[6]^"-"), expression(x[5]^"-"), expression(x[4]^"-"),
  expression(x[3]^"-"), expression(x[2]^"-"), expression(x[1]^"-"),
  expression(x[1]^"+"), expression(x[2]^"+"), expression(x[3]^"+"),
  expression(x[4]^"+"), expression(x[5]^"+"), expression(x[6]^"+")
)
```


# Simulation 1 (new version)

```{r bound2}
file_name <- "boundary_lambda_vary.RDS"
fname <- file.path(dir_name, file_name)

bound_df <- read_rds(fname) %>% 
  rename(method = method_type) %>% 
  select(phi, method, alpha:lambda, Nsim, any_of("early_stop"),
         matches("^x[1-9](pos|neg)_est")) %>% 
  rename_with(\(x) str_remove(x, "_est")) %>% 
  add_column(x0 = 0L, .before = "x1pos")

# Add true value
bound_df <- bound_df %>%
  nest(data = !c(alpha:lambda)) %>%
  rowwise() %>%
  mutate(
    truev = list(
      find_optimal_params(
        params = list(
          "alpha" = alpha, "beta" = beta, "lambda" = lambda, "wp" = 0.5, "wn" = 0.5
          ),
        exp_params_init = exp_param$init_values,
        x_num = exp_param$n_est)
      )
    ) %>%
  ungroup() %>%
  unnest_wider(truev, names_sep = "_") %>%
  select(!matches("truev_(L(_2)?|G_2|lambda_KW)$")) # L, L2 G2 orlambdaKW

# unnest and pivot_longer
true_df <- bound_df %>%
  add_column(truev_x0 = 0) %>% 
  pivot_longer(
    cols = starts_with("truev"), 
    names_to = "utility",
    values_to = "true_value") %>% 
  mutate(utility = utility |>
           str_remove("^truev_")|>
           factor(labels = -6:6,
                  levels =
                    c(paste0("x", 6:1, "neg"),
                      "x0",
                      paste0("x", 1:6, "pos")))
         ) %>% 
  select(!data)

cleaned_df <- bound_df %>%
  select(alpha:data) %>% 
  unnest() %>%
  utility_longer() %>% 
  left_join(true_df, by = join_by(alpha, beta, lambda, utility))

```

## Utility Curve Plots

顏色線段代表 95% 的觀測值分布範圍長度。黑色虛線為實際數值

```{r, fig.height=6.5, fig.width=12}
cleaned_df %>% 
  filter(lambda == 2.25 & phi != "small") %>%
  # filter(lambda == 2.25 ) %>%
  group_by(phi) %>% 
  ggplot(aes(y = utility)) +
  geom_hline(
    yintercept = 
      as.numeric(
        factor("x0",
               levels =
                 c(paste0("x", 6:1, "neg"),
                   "x0",
                   paste0("x", 1:6, "pos")))),
    color = "red2",
    linetype = "dashed", alpha = 0.8) +
  # True utility curve
  geom_line(
    aes(y = utility, x = true_value, group = 1),
    color = "black", linetype = "3331") +
  geom_point(
    aes(y = utility, x = true_value, group = 1),
    color = "black", pch = 1, size =2.5) +
  # 95% range
  stat_summary(
    aes(y = utility, x = x_value, color = phi, shape = phi),
    geom = "pointrange",
    fun = \(x) mean(x, na.rm = TRUE),
    fun.min = \(x) quantile(x, .025, na.rm = TRUE),
    fun.max = \(x) quantile(x, .975, na.rm = TRUE),
    position = position_dodge(width = 0.9),
    linewidth = 1.1, size = 0.6, alpha=.8
  ) +
  labs(x = "Elicited x ", y = "Values", color = "phi") +
  facet_wrap(~ method, dir="v", ncol=5, nrow=2) +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = 16),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14),
    legend.text = element_text(size = 15)) +
  ggtitle(glue("Value Curve"))

pname <- "study1_utility_curve.pdf"

if (!file.exists(file.path(pic_path, pname))) {
  ggsave(filename = pname,
         width = 12,
         height = 6.5,
         units = "in",
         device = "pdf",
         path = pic_path)
} else {
  cat("File already exists. Not saving:", file.path(pic_path, pname), "\n")
}
```

## Bias and RMSE


```{r summ_biasRMSE}
df.bias_RMSE <- cleaned_df %>%
  filter(utility != 0) %>% 
  mutate(
    method = case_when(
      method == "Bisection_Slider" ~ "Bisection-Slider",
      method == "Bisection_Slider_fixbnd" ~ "Bisection-Slider_fixbnd",
      TRUE ~ method # Keep other values unchanged
    ),
    boundary_type = case_when(
      grepl(".*_fixbnd$", method) ~ "fix_bnd",
      grepl(".*_randInit$", method) ~ "rand_init",
      TRUE ~ "equal_exp"
    ),
    method = str_replace(method, "_(randInit|fixbnd)$", "")
  ) %>% 
  group_by(phi, method, boundary_type, utility, lambda) %>% 
  summarise(
   bias = mean(x_value - true_value)|> round(),
   RMSE = 
     (x_value - true_value)^2 |> 
     mean() |>
     sqrt() |>
     round(),
   .groups = "drop"
   )
```

### Bias

```{r bias_bnd, fig.height=7, fig.width=13}
df.bias_RMSE %>% 
  filter(lambda == 2.25) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = bias,
    color = boundary_type,
    group = boundary_type),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = 0, color = "grey30", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = bias,
      color = boundary_type,
      shape = boundary_type),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             # scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_color_discrete(
    # values = c("fix_bnd" = "cyan4", "equal_exp" = "orange2"),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variants") +
  scale_shape_manual(
    values = c("fix_bnd" = 16, "equal_exp" = 17, "rand_init" = 15),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variants") +
  labs(x = "x_i",
       y = "Bias",
       title = "Bias")+
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14),
    legend.text = element_text(size = 15)
    )

pname <- "study1_bias.pdf"

save_fig(pname, width = 13, height = 7)
```


### Bias2

Vary in $\lambda$ in the value function.

-   3 levels: 0.5, 1, 2.25.

```{r bias_vary_lambda, fig.height=7, fig.width=21}
df.tmp <- cleaned_df %>%
  filter(utility != 0) %>% 
  mutate(
    method = case_when(
      method == "Bisection_Slider" ~ "Bisection-Slider",
      method == "Bisection_Slider_fixbnd" ~ "Bisection-Slider_fixbnd",
      TRUE ~ method # Keep other values unchanged
    )
    ) %>% 
  group_by(phi, method, utility, lambda) %>% 
  summarise(
   bias = mean(x_value - true_value)|> round(),
   RMSE = (x_value - true_value)^2 |> 
     mean() |>
     sqrt() |>
     round(),
   .groups = "drop"
   )

df.tmp %>% 
  mutate(lambda = as.factor(lambda)) %>%
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = bias,
    color = lambda,
    group=lambda),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  geom_hline(yintercept = 0, color = "grey30", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = bias,
      color = lambda),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             # scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  labs(x = "x_i",
       y = "Bias",
       title = "Bias (Varies with Lambda)")+
  theme(
    title = element_text(size = 20),
    legend.position = "bottom",
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 14),
    axis.title = element_text(size = 16),
    axis.text.x = element_text(size = 12, vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 12)
    )

pname <- "study1_bias_different_Lambda.pdf"

save_fig(pname, width = 21, height = 7)
rm(df.tmp)
```


### RMSE

```{r RMSE_bnd, fig.height=7, fig.width=13}
df.bias_RMSE %>% 
  filter(lambda == 2.25) %>% 
  ggplot(aes(x = utility)) +
  geom_line(aes(
    x = utility,
    y = RMSE,
    color = boundary_type,
    group = boundary_type),
    linewidth = 1.2,
    alpha = 0.8
    ) +
  # geom_hline(yintercept = c(500,-500), color = "red2", lty=2, alpha=0.8)+
  geom_point(
    aes(
      y = RMSE,
      color = boundary_type,
      shape = boundary_type),
    size = 3) +
  facet_grid(rows = vars(phi),
             cols = vars(method),
             # scales = "free_y"
             ) +
  scale_x_discrete(labels = latex_labels) +
  scale_color_discrete(
    # values = c("fix_bnd" = "cyan4", "equal_exp" = "orange2"),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variants") +
  scale_shape_manual(
    values = c("fix_bnd" = 16, "equal_exp" = 17, "rand_init" = 15),
    labels = c("fix_bnd" = "Boundary Width = 5000",
               "equal_exp" = "Equal Expectation",
               "rand_init" = "Random Initial"),
    name = "Variants") +
  labs(x = "x_i",
       y = "RMSE",
       title = "RMSE")+
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14),
    legend.text = element_text(size = 15)
    )

pname <- "study1_RMSE.pdf"
save_fig(pname, width = 13, height = 7)
```


## Step Count

```{r eval=FALSE, include=FALSE}
len_df <- read_rds(fname) %>% 
  select(alpha:Nsim, ends_with("len")) %>%
  mutate(
    method = str_replace(method_type, "_(randInit|fixbnd)$", ""),
    variant = ifelse(
        grepl(".*_fixbnd$", method_type),
        "fix_bnd",
        ifelse(
          grepl(".*_randInit$", method_type),
          "rand_init",
          "equal_exp")
        ),
    .after = phi,
    .keep = "unused"
  )

len_df %>% 
  group_by(phi, lambda,  method, variant) %>% 
  filter(lambda ==2.25) %>% 
  mutate(
    mean_each_step = rowMeans(across(ends_with("len"))),
    .keep = "unused"
  ) %>%
  summarise(
    mean_step = mean(mean_each_step) |> round(),
    .groups = "drop"
  ) %>% 
  select(!lambda) %>% 
  write_csv(
    file = file.path(pic_path, "step.csv")
  )

```

# Extensions: Loss aversion

## Functions

Functions for computing Loss Aversion esimates
```{r LA_functions}
# functions for computing Loss Aversion estimates

get_minusx_utility <- function(x, data, method = c("interpolation", "power_func"), 
                               alpha = NULL, beta = NULL){
  method <- match.arg(method)
  
  minusx <- - x
  if (method == "interpolation") {
    interpolate_point <- approx(x = sort(c(data$loss, 0, data$gain)), y = -6:6, xout = minusx)
    minusx_utility <- interpolate_point$y
  } else { # method == "power_func"
    minusx_utility <- NA
  }
  
  return(minusx_utility)
}

KT <- function(data, output = c("coefficient", "classification", "all"),
               type = c("median", "mean")){
  output <- match.arg(output)
  type <- match.arg(type)
  
  gain_max <- max(data$gain)
  loss_min <- min(data$loss)
  
  lambda <- data %>% 
    pivot_longer(cols = c(gain, loss), names_to = "domain", values_to = 'x') %>% 
    mutate(utility = (-1)^(domain == "loss") * trial,
           minusx_utility = map_dbl(x, ~ get_minusx_utility(., data)),
           utility_ratio = pmap_dbl(list(domain, utility, minusx_utility), 
                                    ~ switch(..1, 
                                             gain = abs(..3 / ..2),
                                             loss = abs(..2 / ..3)))) %>% 
    summarise(estimate = switch(type, 
                                median = median(utility_ratio, na.rm = TRUE),
                                mean = mean(utility_ratio, na.rm = TRUE)),
              n_reasonable_points = sum(!is.na(utility_ratio)),
              criterion = ceiling(n_reasonable_points / 2),
              n_ratio_greater_1 = sum(utility_ratio > 1, na.rm = TRUE),
              n_ratio_less_1 = sum(utility_ratio < 1, na.rm = TRUE)) %>% 
    mutate(classification = case_when(n_ratio_greater_1 > criterion  ~ "averse",
                                      n_ratio_less_1 > criterion ~ "seeking",
                                      TRUE ~ "neutral"))
  
  if (output == "coefficient") {
    lambda$estimate
  } else if (output == "classification") {
    lambda$classification
  } else {
    lambda
  }
}

KT2 <- function(data){
  gain_max <- max(data$gain)
  loss_min <- min(data$loss)
  
  lambda <- data %>% 
    pivot_longer(cols = c(gain, loss), names_to = "domain", values_to = 'x') %>% 
    mutate(utility = (-1)^(domain == "loss") * trial,
           minusx_utility = map_dbl(x, ~ get_minusx_utility(., data)),
           utility_ratio = pmap_dbl(list(domain, utility, minusx_utility), 
                                    ~ switch(..1, 
                                             gain = abs(..3 / ..2),
                                             loss = abs(..2 / ..3)))) %>% 
    summarise(mean = mean(utility_ratio, na.rm = TRUE),
              median = median(utility_ratio, na.rm = TRUE),
              n_reasonable_points = sum(!is.na(utility_ratio)),
              criterion = ceiling(n_reasonable_points / 2),
              n_ratio_greater_1 = sum(utility_ratio > 1, na.rm = TRUE),
              n_ratio_less_1 = sum(utility_ratio < 1, na.rm = TRUE)) %>% 
    mutate(classification = case_when(n_ratio_greater_1 > criterion  ~ "averse",
                                      n_ratio_less_1 > criterion ~ "seeking",
                                      TRUE ~ "neutral"))
  lambda_list <- lambda %>% 
    select(mean, median, classification) %>% 
    as.list()
  # return
  lambda_list
}
```

## Preprocess

```{r true_LA}
# compute True LA coef. values
trueLA_df <- bound_df %>% 
  select(!data) %>% 
  mutate(KW = - truev_x1pos / truev_x1neg) %>% 
  pivot_longer(cols = matches(".*[1-9][pos|neg]"),
                 names_to = c("trial", "type"),
                 names_pattern = "x(\\d)(.*)",
                 values_to = "value") %>%
  mutate(
    trial = as.integer(trial),
    type = ifelse(type == "pos", "gain", "loss")  # Assign gain/loss
  ) %>% 
  pivot_wider(names_from = type, values_from = value) %>%
  nest(data = c(trial, gain, loss))

trueLA_df <- trueLA_df %>% 
  mutate(
    KT = map(data, ~KT2(.x)),
    .keep = "unused"
    ) %>% 
  unnest_wider(KT, names_sep = "_") %>% 
  pivot_longer(cols = KW:KT_median,
               names_to = "LA_type",
               values_to = "true_LA_est") %>% 
  rename(true_KT_classification = "KT_classification")

```


```{r compute LA}
file_path <- file.path(dir_name, "LA_fixbnd_df.RDS")

if (file.exists(file_path)) {
  LA_result <- read_rds(file_path)
  print(paste("File read from:", file_path))
} else {
  library(furrr)
  LA_result <- bound_df %>% 
    select(!starts_with("true")) %>% 
    unnest() %>% 
    mutate(KW = -x1pos/x1neg)
  
  LA_result <- LA_result %>% 
    pivot_longer(cols = matches(".*[1-9][pos|neg]"),
                   names_to = c("trial", "type"),
                   names_pattern = "x(\\d)(.*)",
                   values_to = "value") %>%
    mutate(
      trial = as.integer(trial),
      type = ifelse(type == "pos", "gain", "loss")  # Assign gain/loss
    ) %>% 
    pivot_wider(names_from = type, values_from = value) %>%
    nest(data = c(trial, gain, loss))
  plan(multisession)
    # Measure system time for paralleled processing
  print(Sys.time())
  tm <- system.time({
    LA_result <- LA_result %>%
      # slice_sample(n = 1000) %>% 
      mutate(
        KT = future_map(data, ~ KT2(.x)),
        .keep = "unused"
        ) %>% 
      unnest_wider(KT, names_sep = "_") %>% 
      pivot_longer(cols = KW:KT_median,
                   names_to = "LA_type",
                   values_to = "LA_est")
    
  })
  print(tm)
  # Save LA_result as an RDS file
  saveRDS(LA_result, file = file_path)
  print(paste("File saved at:", file_path))
}

```

```{r}
LA_summ <- LA_result %>% 
  select(!x0) %>%
  left_join(trueLA_df, by = join_by(alpha, beta, lambda, LA_type)) %>% 
  group_by(lambda, phi, method, LA_type) %>% 
  summarise(
    bias = mean((LA_est - true_LA_est), na.rm = TRUE),
    RMSE = mean((LA_est - true_LA_est)^2, na.rm = TRUE),
    .groups = "drop"
  )
```

```{r eval=FALSE, fig.height=12, fig.width=12, include=FALSE}
LA_result %>%
  select(!x0) %>% 
  left_join(trueLA_df, by = join_by(alpha, beta, lambda, LA_type)) %>% 
  mutate(lambda = factor(lambda)) %>% 
  group_by(lambda, phi, method, LA_type) %>% 
  ggplot() +
  geom_vline(
    aes(xintercept = true_LA_est, color = lambda),
    lty=2, linewidth =1.05
    ) +
  stat_summary(
    aes(x = LA_est, y = method, color = lambda),
    geom = "errorbar",
    position = position_dodge(0.6),
    fun.min = function(x) quantile(x, 0.025, na.rm = TRUE),
    fun.max = function(x) quantile(x, 0.975, na.rm = TRUE),
    linewidth = 1.2
  ) +
  stat_summary(
    aes(x = LA_est, y = method, color = lambda, shape = lambda),
    position = position_dodge(0.8),
    fun = mean,
    geom = "point",
    size = 3.5,
  ) +
  # xlim(0, 6) +
  facet_grid(phi ~ LA_type,
             # labeller = "label_both"
             scales = "free"
            ) +
  labs(x = "Loss Aversion Coefficient",
   y = "Methods",
   color = "Itertation Number",
   shape = "Itertation Number",
   title = "Loss Aversion Coefficients Estimates") +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14)
    )

```

### Bias and RMSE

bias 和 RMSE 都是 ASA 最好


```{r fig.height=10, fig.width=13}
LA_summ  %>% 
  filter(is.finite(bias)) %>% 
  # filter(!method %in% c("MOBS", "PEST", "PEST_randInit")) %>% 
  # filter(early_stop == 10) %>%
  mutate(lambda = as.factor(lambda)) %>%
  ggplot(aes(x = method)) +
  geom_hline(yintercept = 0, color = "grey30", lty = 2, alpha = 0.8) +
  geom_point(aes(y = bias,
               shape = lambda,
               color = lambda,
               group = lambda),
             position = position_dodge(width = 0.4),
             size = 3.0) +
  facet_grid(rows = vars(phi),
             cols = vars(LA_type),
             scales = "free_y"
             ) +
  # scale_y_continuous(breaks = seq(-1, 3.5, .5)) +
  labs(x = "Method",
       y = "Bias",
       color = "Lambda",
       shape = "Lambda",
       title = "Loss Aversion Coefficients: Bias")+
  theme(legend.position = "bottom",
        axis.text.x = element_text(size = 11, angle = 90, vjust = .55),
        legend.title = element_text(size = 16),
        strip.text= element_text(size = 13),
        legend.text = element_text(size = 14),
        title = element_text(size = 18))
```


```{r fig.height=10, fig.width=13}
LA_summ  %>% 
  filter(is.finite(RMSE)) %>% 
  # filter(!method %in% c("MOBS", "PEST", "PEST_randInit")) %>% 
  # filter(early_stop == 10) %>%
  mutate(lambda = as.factor(lambda)) %>%
  ggplot(aes(x = method)) +
  geom_hline(yintercept = 0, color = "grey30", lty = 2, alpha = 0.8) +
  geom_point(aes(y = RMSE,
               shape = lambda,
               color = lambda,
               group = lambda),
             position = position_dodge(width = 0.4),
             size = 3.0) +
  facet_grid(rows = vars(phi),
             cols = vars(LA_type),
             scales = "free_y"
             ) +
  # scale_y_continuous(breaks = seq(-1, 3.5, .5)) +
  labs(x = "Method",
       y = "RMSE",
       color = "Lambda",
       shape = "Lambda",
       title = "Loss Aversion Coefficients: RMSE") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(size = 11, angle = 90, vjust = .55),
        legend.title = element_text(size = 16),
        strip.text= element_text(size = 13),
        legend.text = element_text(size = 14),
        title = element_text(size = 18))
```

---
# References



