---
title: "Simulation Study-2"
author: "Wei-Chen Chang"
date: "`r Sys.Date()`"
output: 
  html_document:
     toc: true
     toc_depth: 2
     toc_float: true
     code-link: true
     code-tools: true
     code_folding: show
     code_download: true
     code-overflow: "scroll"
     self-contained: true
     number_sections: false
     df_print: paged
bibliography: "CPT_LA_new.bib"  
csl: "apa.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.align = "center",
	warning = FALSE,
	rows.print=11,
	paged.print=TRUE
)
```

```{r lib, message=FALSE, include=FALSE}
library(tidyverse)
library(DT)
library(glue)
library(magrittr)
library(patchwork)
library(kableExtra)
# import functions
source(here::here("functions", "player_and_lotteries.R"))
source(here::here("functions", "new_game.R"))
source(here::here("functions", "analysis_functions.R"))
# ggplot settings
theme_set({
  theme_bw()+    
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 17),
    legend.text = element_text(size = 17),
    axis.title = element_text(size = 16),
    axis.text.x = element_text(vjust = 0.5, hjust = 0.5),
    axis.text = element_text(size = 13),
    strip.text= element_text(size = 14),
    title = element_text(size = 18))
})
```


# Introduction

-   回去翻過去 EDP 的實驗資料分析有個奇怪的地方，就是發現不少違反 monotonicity 的受試者

    -  bisection method 決定boundary的方法之一就是採用monotonicity，因此不應該發生這件事。
    
-   重看當時的實驗程式，發現當時的做法和A學者所提Bisection不同，並沒有紀錄upper/lower bound再取中點，而是先用equal expectation決定初始值，直接以初始值的絕對值* 1/2 當作一開始的step size，之後的step size就一直折半下去。

    -  姑且先稱作simplified Bisection (不用modified 是怕跟MOBS搞混)，取`Simp_Bisection`
    
-   EDP 當時測的樣本點比A學者2016年的多，收到 $x_8^+, x_8^-$，且 Iteration = 5。以下模擬也會以這部分為基準進行討論。


## Simulation Overview

-   EDP 裡面 simplified Bisection用的也是固定Iteration = 5的設定，因此根據Study 2的設定，訂定Iteration = 5, 10的情況下進行模擬。比較Study 2 中和其他方法間的差異。

    -   參數設定一樣，固定value function，變動$\phi$

-   因為EDP樣本點較多，模擬也有做到 $x_8^+, x_8^-$額外獨立分析

    -   多做 $\lambda=0.5, 1, 2.25$三個 levels 的模擬比較其 biasedness。
    
    -   分析違反 monotonicity 的比例

# Simulation Setting Codes

```{r params}
# Simulation Parameters
Nsim <-  1000L
.phi <-  0.0367 # err = 1e-8, 0.027513126 is err = 1e-6
param <-  list("alpha"=.88, "beta"=.88, "lambda"=2.25, "wp"=.5, "wn"=.5)
exp_param <- list(
  init_values =
    list("G"= 2000L,
         "g"=300L, "l"=-300L),
  random_init = FALSE,
  fix_bnd_width = FALSE,
  n_est = 3L + (6*2L),
  min_step = 0L,
  step_size = 320L
)
mix_param <- list(
  est_method = "ASA", # changed method type: ASA, UD
  start_crit = 500L, # Bisection 3 Times
  start_step = 100L, # ASA_c = 2*100
  stop_rev_times = 3L,
  UseMidrunEst = TRUE 
) 
phi_vec <-  c(.phi*10, .phi, .phi*0.1)
phi_names <- c("large", "medium","small")

# methods
method_levels <- c(
  as.vector(mapply(function(base, suffix) c(base, paste0(base, suffix)),
         base = c("Bisection", "Bisection-Slider", "MOBS"),
         suffix = "_adaptiveBnd")),
  as.vector(mapply(function(base, suffix) c(base, paste0(base, suffix)),
         base = c("ASA", "PEST", "SimpBisection"),
         suffix = "_randInit")),
  "Bisection-ASA", "Bisection-ASA_adaptiveBnd"
  )

method_labels <- (function(x) {
  x <- gsub("_adaptiveBnd$", "\n(Adaptive Bound)", x)
  x <- gsub("_randInit$",    "\n(Random Initial)", x)
  x
})(method_levels)
```


## Directories


```{r dir_params}
dir_name <- here::here("simulated_data")
pic_path <- "./figs"
```

# Simulation 2 (new)

The simulation data is stored as a `data.frame`, making it easier to process.

-  加上`SimpBisection`，和其他方法比較

## Read file and Preprocess

```{r read_early_stop}
file_name <- "Study2_simulation_20250619_160243.rds"
fname <- file.path(dir_name, file_name)

early_df <- 
  readRDS(fname) %>% 
  separate_wider_delim(
    method_type,
    delim = "_early",
    names = c("method", "early_stop")
    ) %>% 
  select(phi, method, alpha:lambda, Nsim, any_of("early_stop"),
         matches("^x[1-9](pos|neg)_est")) %>% 
  rename_with(\(x) str_remove(x, "_est")) %>% 
  add_column(x0 = 0L, .before = "x1pos")

# Count the invalid points
cat("Invalid data information")
early_df %>%
  group_by(method, lambda, phi, early_stop) %>%
  summarise(
    num_Inf = sum(rowSums(across(x1pos:x6neg, is.infinite)) > 0),
    num_na = sum(rowSums(across(x1pos:x6neg, is.na)) > 0),
            .groups = 'drop'
    ) %>% 
  filter(num_na!=0) %>%
  print()

# Add true value
early_df <- early_df %>%
  # Filter invalid data points
  filter(!rowSums(across(x1pos:x6neg, is.na)) > 0) %>%
  nest(data = !c(alpha:lambda)) %>%
  rowwise() %>%
  mutate(
    truev = list(
      find_optimal_params(
        params = list(
          "alpha" = alpha, "beta" = beta, "lambda" = lambda, "wp" = 0.5, "wn" = 0.5
          ),
        exp_params_init = exp_param$init_values,
        x_num = exp_param$n_est)
      )
    ) %>%
  ungroup() %>%
  unnest_wider(truev, names_sep = "_") %>%
  select(!matches("truev_(L(_2)?|G_2|lambda_KW)$")) # L, L2 G2 orlambdaKW

# unnest and pivot_longer
true_df <- early_df %>%
  add_column(truev_x0 = 0) %>% 
  pivot_longer(
    cols = starts_with("truev"), 
    names_to = "utility",
    values_to = "true_value") %>% 
  mutate(utility = utility |>
           str_remove("^truev_")|>
           factor(labels = -6:6, levels = gen_util_levels())
         ) %>% 
  select(!data)

cleaned_df <- early_df %>%
  select(alpha: data) %>% 
  unnest(data) %>%
  utility_longer() %>% 
  left_join(true_df, by = join_by(alpha, beta, lambda, utility)) %>%
  mutate(method = gsub("_mix", "-", method),
         early_stop = as.numeric(early_stop)
         )
```


## Bias and RMSE


```{r}
early.bias_RMSE <- cleaned_df %>% 
  filter(utility != 0) %>% 
  group_by(phi, method, utility, early_stop, lambda) %>% 
  summarise(
   bias = mean(x_value - true_value)|> round(),
   RMSE = 
     (x_value - true_value)^2 |> 
     mean() |>
     sqrt() |>
     round(),
   .groups = "drop"
   ) %>% 
  mutate(
    method =
      factor(method,
             levels = method_levels,
             labels = method_labels
             ),
    early_stop = as.factor(early_stop)
  )
```

結果如下， simplified Bisection (`Simp_Bisection`) 的結果其實與Bisection差不多，RMSE 在gain domain下會比較大。

### Plot Function 

```{r}
# Define a wrapper function for plotting
plot_early_bias_RMSE <- function(data, y_var, title, hline_value, 
                                 combine_first_two_rows = TRUE, 
                                 global_var_name = NULL) {
  
  # Set default global variable name based on y_var if not provided
  if (is.null(global_var_name)) {
    global_var_name <- paste0("global_y_ranges_", y_var)
  }
  
  # Calculate y-range for phi levels
  y_ranges <- data %>%
    group_by(phi) %>%
    summarise(
      y_min = min(!!sym(y_var), na.rm = TRUE),
      y_max = max(!!sym(y_var), na.rm = TRUE),
      .groups = 'drop'
    )
  
  # Make first two phi levels have the same range (optional)
  if (combine_first_two_rows && nrow(y_ranges) >= 2) {
    combined_min <- min(y_ranges$y_min[1:2])
    combined_max <- max(y_ranges$y_max[1:2])
    y_ranges$y_min[1:2] <- combined_min
    y_ranges$y_max[1:2] <- combined_max
  }
  
  # For separate plots (when data is filtered), use global ranges from the original full dataset
  # This ensures consistent scaling across separate plots
  if (!exists(global_var_name, envir = .GlobalEnv)) {
    # Store global ranges in the global environment for separate plots to use
    assign(global_var_name, y_ranges, envir = .GlobalEnv)
  }
  
  # Use global ranges if they exist (for separate plots)
  if (exists(global_var_name, envir = .GlobalEnv)) {
    y_ranges_to_use <- get(global_var_name, envir = .GlobalEnv)
    # Match the phi levels present in current data with global ranges
    y_ranges <- y_ranges %>%
      select(phi) %>%
      left_join(y_ranges_to_use %>% select(phi, y_min, y_max), by = "phi")
  }
  
  # Add y-range info to data
  data_with_ranges <- data %>%
    left_join(y_ranges, by = "phi")
  
  ggplot(data_with_ranges, aes(x = utility)) +
    geom_line(aes(
      x = utility,
      y = !!sym(y_var),
      color = early_stop,
      group = early_stop),
      linewidth = 1.2,
      alpha = 0.8
    ) +
    geom_hline(yintercept = hline_value, color = "grey20", lty=2, alpha=0.8) +
    geom_point(
      aes(
        y = !!sym(y_var),
        color = early_stop,
        shape = early_stop),
      size = 3
    ) +
    # Add invisible points to force consistent y-axis ranges within each row
    geom_point(aes(y = y_min), alpha = 0, size = 0) +
    geom_point(aes(y = y_max), alpha = 0, size = 0) +
    facet_grid(rows = vars(phi),
               cols = vars(method),
               scales = "free_y"
    ) +
    scale_x_discrete(labels = latex_labels) +
    scale_shape_manual(
      values = c("5" = 16, "10" = 17)) +
    labs(
      x = expression(x[i]),
      y = title,
      color = "Iteration Number",
      shape = "Iteration Number",
      title = paste(title, "(Fixed Iteration)")
    ) +
    theme(
      axis.text.y = element_text(size=14)
    )
}
```


### bias
```{r rRMSE_early, fig.height=6, fig.width=24}
p.bias <- early.bias_RMSE %>% 
  plot_early_bias_RMSE("bias", "Bias", 0)

pname <- "study2_relativeRMSE.pdf"
save_fig(pname, width = 18, height = 6)

```

### relative RMSE

```{r rRMSE_early, fig.height=6, fig.width=24}
p.RMSE <- early.bias_RMSE %>% 
  plot_early_bias_RMSE("RMSE", "RMSE", 0)

pname <- "study2_relativeRMSE.pdf"
save_fig(pname, width = 18, height = 6)

```

### relative RMSE

```{r rRMSE_early, fig.height=6, fig.width=24}
p.rRMSE <- early.bias_RMSE %>% 
  group_by(phi, utility, early_stop) %>%
  mutate(
    relative_RMSE = RMSE / RMSE[method == "Bisection"],
    early_stop = as.factor(early_stop)
  ) %>% 
  filter(method != "Bisection") %>% 
  plot_early_bias_RMSE("relative_RMSE", "Relative RMSE to Biscetion", 1)

pname <- "study2_relativeRMSE.pdf"
save_fig(pname, width = 18, height = 6)

```




## Combined plot

### Bias

```{r, fig.height=13, fig.width=14}
# First, ensure global ranges are calculated from the full dataset for bias
# This creates the global_y_ranges_bias that both plots will use
# combine_first_two_rows = TRUE means first two rows will have the same range
invisible(early.bias_RMSE %>% 
  plot_early_bias_RMSE("bias", "Bias", 0, 
                       combine_first_two_rows = TRUE, 
                       global_var_name = "global_y_ranges_bias"))

p.bias1 <- early.bias_RMSE %>% 
  filter(grepl("^(Bisection)|(MOBS)", method)) %>%
  plot_early_bias_RMSE("bias", "Bias", 0, 
                       combine_first_two_rows = TRUE, 
                       global_var_name = "global_y_ranges_bias") +
  ggtitle("Bisection-based Methods") +
  theme(title = element_text(size = 16))

p.bias2 <- early.bias_RMSE %>% 
  filter(!grepl("^(Bisection)|(MOBS)", method)) %>%
  plot_early_bias_RMSE("bias", "Bias", 0, 
                       combine_first_two_rows = TRUE, 
                       global_var_name = "global_y_ranges_bias") +
  ggtitle("Non-bisection Methods and SimpBisection") +
  theme(title = element_text(size = 16))

p.bias1 / p.bias2  +
  plot_annotation(
    title = 'Bias in Study 2: Fixed Number of Iterations',
    theme = theme(plot.title = element_text(size = 28, hjust = .5))) +
  plot_layout(guides = 'collect',
              axes = 'collect'  # This collects both x and y axes
              )
```

```{r, fig.height=13, fig.width=14}
# First, ensure global ranges are calculated from the full dataset for RMSE
# This creates separate global ranges for RMSE (different from bias)
# combine_first_two_rows = FALSE means each row will have its own optimal range
invisible(early.bias_RMSE %>% 
  plot_early_bias_RMSE("RMSE", "RMSE", 0, 
                       combine_first_two_rows = FALSE, 
                       global_var_name = "global_y_ranges_RMSE"))

p.RMSE1 <- early.bias_RMSE %>% 
  filter(grepl("^(Bisection)|(MOBS)", method)) %>%
  plot_early_bias_RMSE("RMSE", "RMSE", 0, 
                       combine_first_two_rows = FALSE, 
                       global_var_name = "global_y_ranges_RMSE") +
  ggtitle("Bisection-based Methods") +
  theme(title = element_text(size = 16))

p.RMSE2 <- early.bias_RMSE %>% 
  filter(!grepl("^(Bisection)|(MOBS)", method)) %>%
  plot_early_bias_RMSE("RMSE", "RMSE", 0, 
                       combine_first_two_rows = FALSE, 
                       global_var_name = "global_y_ranges_RMSE") +
  ggtitle("Non-bisection Methods and SimpBisection") +
  theme(title = element_text(size = 16))

p.RMSE1 / p.RMSE2  +
  plot_annotation(
    title = 'RMSE in Study 2: Fixed Number of Iterations',
    theme = theme(plot.title = element_text(size = 28, hjust = .5))) +
  plot_layout(guides = 'collect',
              axes = 'collect'  # This collects both x and y axes
              )
```

### Relative RMSE

```{r, fig.height=13, fig.width=14}
df.rRMSE <- early.bias_RMSE %>% 
  group_by(phi, utility, early_stop) %>%
  mutate(
    relative_RMSE = RMSE / RMSE[method == "Bisection"],
    early_stop = as.factor(early_stop)
  ) %>% 
  filter(method != "Bisection")


invisible(df.rRMSE %>% 
  plot_early_bias_RMSE("relative_RMSE", "", 1, 
                       combine_first_two_rows = FALSE, 
                       global_var_name = "global_y_ranges_relativeRMSE"))


# plot_early_bias_RMSE("relative_RMSE", "Relative RMSE to Biscetion", 1)


p.rRMSE1 <- df.rRMSE %>% 
  filter(grepl("^(Bisection)|(MOBS)", method)) %>%
  plot_early_bias_RMSE("relative_RMSE", "Relative RMSE", 1, 
                       combine_first_two_rows = FALSE, 
                       global_var_name = "global_y_ranges_relativeRMSE") +
  ggtitle("Bisection-based Methods") +
  theme(title = element_text(size = 16))

p.rRMSE2 <- df.rRMSE %>% 
  filter(!grepl("^(Bisection)|(MOBS)", method)) %>%
  plot_early_bias_RMSE("relative_RMSE", "Relative RMSE", 1, 
                       combine_first_two_rows = FALSE, 
                       global_var_name = "global_y_ranges_relativeRMSE") +
  ggtitle("Non-bisection Methods and SimpBisection") +
  theme(title = element_text(size = 16))

p.rRMSE1 / p.rRMSE2  +
  plot_annotation(
    title = 'Relative RMSE to Bisection in Study 2',
    theme = theme(plot.title = element_text(size = 28, hjust = .5))) +
  plot_layout(guides = 'collect',
              axes = 'collect'  # This collects both x and y axes
              )
```


## Loss Aversion

- 除了在 $\phi$ 很小的情況下，SimpBisection 表現跟Bisection法差不多。

    -   結果有點亂，不好討論。

### Preprocess

```{r early_LA}
# compute True LA coef. values
trueLA_df <- early_df %>% 
  select(!data) %>% 
  mutate(KW = - truev_x1pos / truev_x1neg) %>%
  pivot_longer(cols = matches(".*[1-9][pos|neg]"),
                 names_to = c("trial", "type"),
                 names_pattern = "x(\\d)(.*)",
                 values_to = "value") %>%
  mutate(
    trial = as.integer(trial),
    type = ifelse(type == "pos", "gain", "loss")  # Assign gain/loss
  ) %>% 
  pivot_wider(names_from = type, values_from = value) %>%
  nest(data = c(trial, gain, loss))

trueLA_df <- trueLA_df %>% 
  mutate(
    KT = map(data, ~ KT2(.x)),
    .keep = "unused"
    ) %>%
  unnest_wider(KT, names_sep = "_") %>% 
  pivot_longer(cols = KW:KT_median,
               names_to = "LA_type",
               values_to = "true_LA_est") %>%
  rename(true_KT_classification = "KT_classification")
```

### Compute LA coef from simulation data

```{r LA2}
file_path <- file.path(dir_name, "Study2_LA_df.RDS")

if (file.exists(file_path)) {
  LA_result <- read_rds(file_path)
  print(paste("File read from:", file_path))
} else {
  library(furrr)
  LA_result <- early_df %>% 
    select(!starts_with("true")) %>% 
    unnest(cols = c(data)) %>% 
    mutate(KW = -x1pos/x1neg)
  
  LA_result <- LA_result %>% 
    pivot_longer(cols = matches(".*[1-9][pos|neg]"),
                   names_to = c("trial", "type"),
                   names_pattern = "x(\\d)(.*)",
                   values_to = "value") %>%
    mutate(
      trial = as.integer(trial),
      type = ifelse(type == "pos", "gain", "loss")  # Assign gain/loss
    ) %>% 
    pivot_wider(names_from = type, values_from = value) %>%
    nest(data = c(trial, gain, loss))
  plan(multisession)
    # Measure system time for paralleled processing
  print(Sys.time())
  tm <- system.time({
    LA_result <- LA_result %>%
      # slice_sample(n = 500) %>%
      mutate(
        # stores median, mean and classification of KT
        # this may cause duplication in interpolation `approx` function
        KT = future_map(data, ~ KT2(.x)),
        .keep = "unused" 
      ) %>%
      unnest_wider(KT, names_sep = "_") %>% 
      pivot_longer(cols = KW:KT_median,
                   names_to = "LA_type",
                   values_to = "LA_est")
  })
  print(tm)
  # Save LA_result as an RDS file
  saveRDS(LA_result, file = file_path)
  print(paste("File saved at:", file_path))
}

```


```{r}
# file_path <- file.path(dir_name, "LA_reslut_df_early.RDS")
# LA_result <- read_rds(file_path)
LA_result <- LA_result %>%
  select(!x0) %>% 
  left_join(trueLA_df, by = join_by(alpha, beta, lambda, LA_type)) %>% 
  mutate(
    early_stop = as.numeric(early_stop),
    method = case_when(
      method == "Bisection_mixASA" ~ "Bisection-ASA",
      TRUE ~ method # Keep other values unchanged
      ),
    method =
      factor(method,
             levels = method_levels
             )
    )
```


### 95% CI

```{r include=FALSE}
custom_shapes <- c(rep(21, 3), 24, 24, 25,25, 22, 22, 21)
names(custom_shapes) <- method_levels
```


```{r funcLA}
##
plot_LA_estimates <- function(data, subset_filter) {
  data %>%
    filter({{ subset_filter }},
           is.finite(LA_est),
           early_stop == 10,
           LA_type != "KT_reg") %>%
    mutate(early_stop = factor(as.numeric(early_stop))) %>%
    group_by(phi, method, LA_type, early_stop) %>%
    ggplot() +
    geom_vline(
      aes(xintercept = true_LA_est),
      lty = 2, color = "grey30", linewidth = 1.05
    ) +
    stat_summary(
      aes(x = LA_est, y = method, color = method),
      geom = "errorbar",
      position = position_dodge(0.6),
      fun.min = \(x) quantile(x, 0.025, na.rm = TRUE),
      fun.max = \(x) quantile(x, 0.975, na.rm = TRUE),
      linewidth = 1.2, width = 0.5
    ) +
    stat_summary(
      aes(x = LA_est, y = method, fill = method, shape = method, color = method),
      position = position_dodge(0.6),
      fun = \(x) mean(x, na.rm = TRUE),
      geom = "point",
      size = 3.0
    ) +
    facet_grid(phi ~ LA_type, scales = "free") +
    scale_x_continuous(
      transform = scales::pseudo_log_trans(base = 10),
      breaks = c(-20, -10, -5, 0, 1, 5, 10, 20, 40)
    ) +
    scale_shape_manual(values = custom_shapes) +   # Custom shape mapping
    labs(
      x = "Loss Aversion Coefficient",
      y = "Methods",
      title = "Loss Aversion Coefficients Estimates (Iteration = 10)"
    ) +
    theme(
      panel.spacing.x = grid::unit(1, "lines"),     # Adjusts horizontal spacing
      legend.title = element_blank(),
      legend.text = element_text(size = 14)
    )
}
```


```{r fig.height=9, fig.width=10}
# filtered
LA_result %>%
  plot_LA_estimates(!grepl("randInit$", method))
pname <- "study2_LA_Summary_iter10woRandInit.pdf"
save_fig(pname, width = 10, height = 9)

LA_result %>%
  plot_LA_estimates() +
  labs(
    title = "Loss Aversion Coefficients Estimates (Iteration = 10, All Methods)"
  )
pname <- "study2_LA_Summary_iter10.pdf"
save_fig(pname, width = 11, height = 9)
```

### Bias and RMSE

```{r}
LA_summ <- LA_result %>% 
  filter(is.finite(LA_est)) %>%  
  # filter(!grepl("randInit$", method)) %>%
  group_by(lambda, phi, method, LA_type, early_stop) %>% 
  summarise(
    bias = mean((LA_est - true_LA_est), na.rm = TRUE),
    RMSE = mean((LA_est - true_LA_est)^2, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  group_by(phi, LA_type, early_stop) %>% 
  mutate(relative_RMSE = RMSE / RMSE[method == "Bisection"]) %>% 
  ungroup()
```

```{r plot_LA}
plot_LA <- function(data, var_y, subset_filter) {
  y_label <- rlang::as_label(rlang::enquo(var_y)) %>%   # Convert to string
    stringr::str_to_sentence()
  
  data %>%
    filter({{ subset_filter }},
           is.finite({{ var_y }}),
           early_stop == 10,
           LA_type != "KT_reg") %>%
    mutate(early_stop = as.factor(early_stop)) %>%
    ggplot(aes(x = method)) +
    geom_hline(yintercept = 0, color = "grey30", lty = 2, alpha = 0.8) +
    geom_point(
      aes(y = {{ var_y }}, fill = method, color = method, shape = method),
      position = position_dodge(width = 0.4),
      size = 3.0
    ) +
    facet_grid(
      rows = vars(phi),
      cols = vars(LA_type),
      scales = "free_y"
    ) +
    scale_shape_manual(values = custom_shapes) +
    labs(
      x = "Method",
      y = y_label,
      title = glue("Loss Aversion Coefficients: {y_label} (Iteration = 10)")
    ) +
    theme(
      legend.title = element_blank(),
      legend.text = element_text(size = 14),
      axis.text.x = element_text(size = 11, angle = 90, vjust = 0.55),
      strip.text = element_text(size = 13)
    )
}
```

```{r, fig.height=9, fig.width=9}
LA_summ %>% 
  plot_LA(bias, !grepl("randInit$", method))
pname <- "study2_LA_bias_iter10woRandInit.pdf"
save_fig(pname, width = 9, height = 9)

LA_summ %>% 
  plot_LA(bias)
pname <- "study2_LA_bias_iter10.pdf"
save_fig(pname, width = 10, height = 9)
```

The cell below shows alternative visualization:

```{r eval=FALSE, fig.width=8, include=FALSE}
# Filter and prepare data
filtered_data <- LA_summ %>%
  filter(is.finite(bias) & early_stop == 10 & LA_type != "KT_reg") %>%
  mutate(early_stop = as.factor(early_stop))

# Define unique facets
facets <- unique(filtered_data %>% select(phi, LA_type))

# Create a list to store individual plots
plot_list <- list()

# Loop over each facet combination
for (i in 1:nrow(facets)) {
  facet_data <- filtered_data %>%
    filter(phi == facets$phi[i], LA_type == facets$LA_type[i])
  
  y_limits <- if (i <= 6) c(-0.5, 1) else c(-2, 4)
  
  p <- ggplot(facet_data, aes(x = method)) +
    geom_hline(yintercept = 0, color = "grey30", lty = 2, alpha = 0.8) +
    geom_point(aes(y = bias, fill = method, color = method, shape = method),
               position = position_dodge(width = 0.4),
               size = 3.0) +
    scale_shape_manual(values = custom_shapes) +  # Custom shape mapping
    labs(x = "Method",
         y = "Bias",
         title = glue("Phi:{facets$phi[i]}; {facets$LA_type[i]}")
         ) +
    ylim(y_limits)+
  # ylim(-1, 1)+  # Set your desired y-axis limits here
    theme(
      # legend.position = "bottom",
      legend.title = element_blank(),
      axis.text.x = element_text(size = 11, angle = 90, vjust = .55),
      strip.text= element_text(size = 11),
      title = element_text(size = 10))
  
  plot_list[[i]] <- p
}

# Combine plots using patchwork
combined_plot <- wrap_plots(
  plot_list,
  ncol = length(unique(filtered_data$LA_type))) +
  plot_annotation(title = "Loss Aversion Coefficients: Bias (Iteration = 10)") +
  plot_layout(axes = "collect",guides = 'collect') &
  theme(legend.position='bottom')
combined_plot
```


#### RMSE

```{r, rows.print=10}
# simply shows the data table
LA_summ %>% 
  filter(early_stop==10) %>% 
  select(!c(lambda, bias)) %>% 
  arrange(phi, LA_type, RMSE)
```

```{r, fig.height=9, fig.width=10}
LA_summ %>% 
  plot_LA(RMSE, !grepl("randInit$", method)) +
  labs(
    y = 'RMSE',
    title = "Loss Aversion Coefficients: RMSE (Iteration = 10)"
  )
pname <- "study2_LA_RMSE_iter10woRandInit.pdf"
save_fig(pname, width = 9, height = 9)

LA_summ %>% 
  plot_LA(RMSE) +
  labs(
    y = 'RMSE',
    title = "Loss Aversion Coefficients: RMSE (Iteration = 10)"
  )
pname <- "study2_LA_RMSE_iter10.pdf"
save_fig(pname, width = 10, height = 9)
```


## Violations of Monotonicity

-   EDP stage 1 的違反比率非常高 (20/87 當取到$x_8$, 14/87當取到$x_6$)。
    
    -  有一可能也是我們測的樣本點太多。

-   但 simplified Bisection 除了$\phi$ small 時特別高，其他都在3%以下。
    
    -   另外違反率大小在目前設定下看起來跟$\lambda$ (i.e., value function)沒有關係，只跟 $\phi$ 有關係。
    
    -   從模型角度來看就是因為我們收的受試者選擇較隨機 ($\phi$較小)而非其他緣故

### Simulation results

-   Simplified-Bisection 在 $\phi$ small 時的違反monotonicity比率甚至比PEST還要誇張。

-   這也能部份解釋 EDP 當時違反monotonicity的情況很嚴重，代表此方法容易導致違反monotonicity。
    
-   過去研究中資料違反 monotonicity/stochastic dominance 的比率 (兩者皆使用 3+1 次 iterations 的bisection-slider法)

    -   A學者(2016) 違反stochastic dominance 比例(3/75 = `r round(3/75, 3)`)

    -   Bleichrod and L’Haridon (2023) 違反stochastic dominance 比例(10/122 = `r round(10/122, 3)`)

```{r paged.print=TRUE, rows.print=9*2}
monotone_df <- cleaned_df %>% 
  select(!true_value) %>% 
  mutate(utility = as.integer(utility) - 7L) %>% 
  pivot_wider(
    names_from = utility,
    values_from = x_value,
    names_glue = "x{abs(utility)}{case_when(utility > 0 ~ 'pos', 
                                       utility < 0 ~ 'neg', 
                                       TRUE ~ '')}"
  ) %>% 
  relocate(gen_util_levels(6L, FALSE), .after = x0) %>% 
  rowwise() %>%
  mutate(
    violation = is.unsorted(c_across(x6neg:x6pos)),
    ) %>%
  ungroup()

monotone_df %>% 
  mutate(early_stop = as.numeric(early_stop),
         method = factor(method, levels = method_levels)
         ) %>% 
  group_by(phi, early_stop, method) %>%
  summarise(
    # n = n(),
    violation_ratio = glue("{round(sum(violation)/n()*100,1)}%"),
    .groups = "drop"
    ) %>%
  pivot_wider(
    names_from = early_stop,
    names_glue = "Iteration = {early_stop}",
    values_from = violation_ratio
  ) %>% 
  filter(!(`Iteration = 5` == "0%" & `Iteration = 10` == "0%")) %>% 
  xtable::xtable()
```


# 小節

-   EDP 中 simplified Bisection 法在受試者選擇較一致時與Bisection法的表現差不多，但是在 $\phi$ 很小的時候表現非常差。
  
    -   RMSE 較大(在gain frame)，且違反monotonicity的比例較高。

-   在 EDP 實驗中產生比較多違反monotonicity的受試者，可能的解釋之一是有許多受試者選擇隨機性較高。
    
    -   違反monotonicity如果只和 $\phi$ 有關而和value function無關，或許可以從這方面去推估實驗$\phi$的數值。



